### 2014-06-06 paper/body.tex
copied from LISA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

It has recently become possible to train much larger artificial neural networks than ever before.

\editbox{write some intro fluff here vvvv}

Recent progress, enabled by Convnets \cite{LeCun89}

these new large networks are breaking previous performance records handily. Also unsupervised work: \cite{Le-2011-ICA} trained large unsupervised network using...

Most of these use combinations of learned convolutional features, pooling over fixed local regions, and normalization of responses based on the responses of other units in the same layer (a basic form of inhibition or local competition, which has a similar effect to ``explaining away'')

(speculation) It is interesting to think that, while we previously fought in a regime where mostly we tried to push performance, and most small performance gains well understood -- that is, the field of machine learning was largely a art of synthesizing functions that worked better and better -- we may soon be entering an era of the field where we have things that are so large and work so well that the performance will outpace our understanding. This will push the  field into a decidedly different regime, one of almost observational science where we merely poke things that work magically well to slowly remove their mystique.

Grand speculation aside, here we seek to understand a few properties of one of the larger class of convolutional neural networks trained using supervised backprop.

((examples))
((diff datasets))
((but same features!))

(((( two gabor features from very different networks ))))

\editbox{write some intro fluff here ----}

Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}). This happens with such frequency that not only is it no longer surprising, but to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a bug somewhere in one's code. In fact, this paper's authors are now used to checking for gabor features in the first layer simply to assure ourselves that the training is at least partially working.

Because finding gabor features on the first layer seems to occur regardless of the exact cost function and natural image dataset used, we may call these these features \emph{general}. On the other hand, we know that the last layer of a trained network will depend greatly on the chosen \{network model, dataset\} combination. For example, for networks trained toward a supervised classification objective, each output unit will be specific to a particular class, at least to the extent that training is successful. In this sense, let's say that the last layer features are \emph{specific}. So far these terms are only intuitively defined, but we shall give one possible more rigorous definition soon.

If the layer 1 features are general, and the last layer features are specific, we know that somewhere in the network there must be a transition from general to specific. This observation raises a few questions:

\begin{itemize}
	\item Can we quantify the degree to which a particular layer is general or specific?
	\item For a particular deep network, does the transition occur suddenly from layer $n$ to $n+1$, or is it spread out over several layers?
	\item Where does this transition take place: near the bottom, middle, or top of the network?
\end{itemize}

Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task. The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task. When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen. In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch. These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.

In this paper we make several contributions:

\begin{enumerate}
\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}). We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves. In different regions of the network, different effects dominate.
\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical.
\end{enumerate}

\edit{talk a little about related work?}

subsection{Related Work (no heading, just group with Intro?)}

Others have loosely addressed the question of generaltiy by showing how features from layers 5/6/7 can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we're aiming for something slightly different: to observe the general to specific transition more directly, if possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Defining Generality vs. Specificity}
\label{sec:definition}

We have noted the curious tendency of gabor features to show up in the first layer of neural networks trained on natural images for a large range of network architectures and cost functions. We say these features are general if they are useful for many different tasks or specific if they are useful only for a few. We can measure the specificity of a set of features by training it on one task \dA and then using it for another task \dB.

Of course, this definition depends on the distance between \dA and \dB. In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset.  \edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.

The dataset we use is from the ImageNet Large Scale Visual Recognition Challenge 2012 (ILSVRC2012) \citep{imagenet_cvpr09}. It contains 1,281,167 labeled training images and 50,000 test images. Each image in the training and validation sets is labeled with one of 1000 classes.
To create tasks \dA and \dB, we randomly split the 1000 classes into two groups, \dA and \dB, each containing 500 classes and approximately half of the data, or about 645,000 examples each. We train one convolutional net on the half-dataset \dA and one on the half-dataset \dB. These networks, which we call \net{baseA} and \net{baseB}, are shown in the top two positions of Figure~\ref{fig:transfer}.

All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{} except for the last softmax layer, which outputs 500 classes instead of 1000.

We then choose an $n$ from $\{1, 2, \ldots, 7\}$ and train several networks. To make the discussion more concrete, let's pick for now $n=3$ (Figure~\ref{fig:transfer} also shows the $n=3$ case). First we train

\begin{itemize}
\item A control network \net{R3B} with the first $3$ layers fixed to random filters and all higher layers trained to classify images from dataset \dB.
\end{itemize}

Then we define and train the following two networks

\begin{itemize}
\item A \emph{selffer} network \net{B3B} where the first $3$ layers are copied from \net{baseB} and frozen. The five higher layers are initialized randomly and trained toward dataset \dB. Here we're only using data from \dB and layers from a network \net{baseB}, that was trained on \dB. This may seem a little strange, but we actually need it as an additional control for the below transfer network.

\item A \emph{transfer} network \net{A3B} where the first $3$ layers are copied from \net{baseA} and frozen. The five higher layers are initialized randomly and trained toward dataset \dB. Intuitively, here we're copying the first $3$ layers from the wrong dataset, \dA,  and then trying to learn higher layer features on top of them to classify \dB. If this works well, we'll say that those first three layers are general, at least with respect to \dB, and if not, we'll say they are specific to dataset \dA
\end{itemize}

Finally, we also train fine-tuned versions of the two above networks:

\begin{itemize}
\item A \emph{selffer} network \net{B3B+} just like \net{B3B}, but where all layers learn
\item A \emph{transfer} network \net{A3B+} just like \net{A3B}, but where all layers learn
\end{itemize}

Figure~\ref{fig:transfer} shows the networks created for $n = 3$, but we repeated this process for all $n$ in $\{1, 2, \ldots, 7\}$\footnote{Note that $n=8$ doesn't make sense in any case: \net{B8B} is just \net{baseB}, \net{R8B} is just a completely retrained version of \net{baseB}, and \net{A8B} would have no hope of working, because nothing would be trained and the 500 softmax neurons would not match between \dA and \dB.} and in both directions, i.e. transferring from \dA to \dB and \dB to \dA.

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{\edit{Caption here...}}
\label{fig:transfer}
\end{figure}

\section{Details of Experiment}

Since \cite{Krizhevsky-2012} won the ImageNet 2012 competition, there has naturally been much interest and work toward tweaking hyperparameters of large convolutional models. For example, \cite{Zeiler+et+al-arxiv2013b} found that it is better to decrease the first layer filters sizes from $11x11$ to $7x7$ and to use a smaller stride of $2$ instead of $4$. When beginning this study we faced the decision of exactly which convolutional architecture to use for our experiments. We decided to use the original architecture from \cite{Krizhevsky-2012} not to maximize absolute performance, but to study transfer results on what is probably the most popular single architecture, so that our results will be comparable, extensible, and useful to the largest number of other researchers. We actually expect none of the qualitative results presented here to depend at all on small architecture tweaks.

To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \cite{donahue+jia-2013-arxiv}. We followed \cite{donahue+jia-2013-arxiv} in making a few minor departures from \cite{Krizhevsky-2012}: we skip the data augmentation trick of adding random multiples of principle components of pixel RGB values, which produced only a $1\%$ improvement in the original paper, and we warped images to $256x256$ instead of scaling to keep the aspect ratio and then cropping. In another difference, we placed the Local Response Normalization layers just \emph{after} the pooling layers, instead of before them. As in previous studies, we use Dropout \citep{Hinton-et-al-arxiv2012} on fully connected layers except for the softmax output layer.

For clarity of presentation, we list all hyperparameter selections in two tables: layer sizes and locations in Table~\ref{tab:network_architecture} and weight initialization and learning rate details in Table~\ref{tab:learning_hyperparams}. In the first table, a feedforward pass proceeds from top to bottom, left to right. Because code is often more clear than text, we've also made all code and parameter files necessary to reproduce these experiments available on \url{http://github.com/...removed_for_review...}.

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[t]
\caption{Parameter initializations and learning rates}
\label{tab:learning_hyperparams}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|}
\hline
       & \multicolumn{3}{c|}{\bf Weight}     &  \multicolumn{3}{c|}{\bf Bias}       \\
\cline{2-7}
       & gaus   & LR-mult & decay &  const  & LR  & decay \\
\hline
conv1  & .01    & 1       & y     &  0      & 2   & n     \\
conv2  & .01    & 1       & y     &  1      & 2   & n     \\
conv3  & .01    & 1       & y     &  0      & 2   & n     \\
conv4  & .01    & 1       & y     &  1      & 2   & n     \\
conv5  & .01    & 1       & y     &  1      & 2   & n     \\
fc6    & .005   & 1       & y     &  1      & 2   & n     \\
fc7    & .005   & 1       & y     &  1      & 2   & n     \\
fc8    & .01    & 1       & y     &  0      & 2   & n     \\ 
\hline
\end{tabular}
\end{center}
\end{table}

We used stochastic gradient descent (SGD) with momentum. Each iteration of SGD used a batch size of 256, momentum 0.9, and multiplicative weight decay (for those weights with weight decay enabled) of 0.0005 per iteration.

For the bulk of the experiments in this paper, the master learning rate was started at 0.01, annealed over the course of training by dropping it by a factor of 10 every 100,000 iterations, and learning was stopped after 450,000 iterations. All training was done on NVidia K20 GPUs. Each iteration took about 1.7 seconds, meaning that the whole training procedure for a single network takes 9.5 days.

Because occupying a whole GPU for this long was cumbersome, we also devised a set of hyperparameters to allow faster learning by boosting the learning rate by 25\% to 0.0125, annealing by a factor of 10 after only 64,000 iterations, and stopping after 200,000 iterations. These selections were made after looking at the learning curves for the base case and estimating at which points in each region of constant learning rate the learning had plateaued and thus annealing could take place.  A typical learning curve is shown in Figure~\ref{typical_learning}.

\editbox{
Figure {typical\_learning}
(( make this figure, if important, once reduced-1300-2 run is done ))
}

Our base model attains a final top-1 error on the validation set of 42.5\%, about the same as the 42.9\% reported by \cite{donahue+jia-2013-arxiv} and 1.8\% worse than \cite{Krizhevsky-2012}, the latter difference probably due to the few minor training differences. We checked these values only to demonstrate that the network was converging reasonably. As our goal is not to improve the state of the art, but to investigate properties of transfer, we were content with this level of performance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Transfer Results and Discussion}
\label{sec:experiments}

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{plots/result_transfer_crop.pdf}
\includegraphics[width=1\linewidth]{plots/result_transfer_lines_crop.pdf}
\end{center}
\caption{\edit{Caption here...}}
\label{fig:results}
\end{figure}

The results of all transfer learning experiments are shown in condensed form in Figure~\ref{fig:results}. Each dot in the figure represents the average accuracy over the validation set for an entire trained network. The black dots above $n=0$ represent the accuracy of \net{baseA} or \net{baseB}. There are eight points, because we made four separate random \net{A}/\net{B} splits. Each dark blue dot represents an \net{AnA} network\footnote{Actually these dots represent \net{AnA} nets or \net{BnB} nets, the statistics of which are equivalent, because in both cases the net is trained on the same random 500 classes. To simplify notation, we'll just calling these \net{AnA} networks. Similarly, we've aggregated the \net{BnA} and \net{AnB} networks and just call them \net{BnA}}, that is, a network that was trained on dataset \dA, chopped off at layer $n$, and then whose upper layers were reinitialized and retrained toward dataset \dA while the lower layers remained frozen. The light blue points represent \net{AnA+} networks, the same as \net{AnA} but where the lower layers were trained as well. Each dark red dot represents a \net{BnA} network, one whose first $n$ layers are copied from \net{baseB} and frozen, and then whose upper layers were randomly initialized and trained toward dataset \dA. The light red points represent \net{BnA+} networks where all layers were fine-tuned.

In the top subplot plot we've shifted each type of point slightly to the left or write simply for visual clarity; if not for this shift they would all be shown directly above $n=1$, $n=2$, etc. and would overlap. In the bottom subplot we've average the results at each layer to show more clearly the overall trend and to highlight the three important effects.

It turns out we can conclude quite a lot from these results! In each of the following interpretations, we compare the performance to the base case (black dots).

\begin{enumerate}

\item The black \net{baseA} points show that the mean performance of a network simply trained to classify a random subset of 500 classes attains a top-1 accuracy of 0.625, or 37.5\% top-1 error. This is different than the 42.5\% top-1 error attained on the 1000 class network for two a combination of two reasons: it is pushed higher because the network is trained only on half of the data, which could lead to more overfit, and it is pushed lower because there are only 500 classes, so there are only half as many ways to make mistakes. It is this latter effect that dominates, leading to lower error overall.

\item The dark blue \net{AnA} points show a curious behavior. We can see at layer one that the performance is the same (as the \net{baseA} points), which was expected. If we learn eight layers of features, save the first layer of learned gabor features, and reinitialize the whole network and retrain it toward the same task, we'd expect to do just as well. This is also true for layer 2. Layers 3, 4, 5, and 6, particularly 4 and 5, behave somewhat differently. When we keep the first, say, 5 layers and retrain layers 6-8, performance suffers. This is evidence that the original network contained \emph{co-adapted features} on successive layers, that is features that interact with each other in a complex way such that this co-adaptation \emph{could not be relearned} by the upper layers. In other words, gradient descent was able to find a good solution the first time, but this was only possible because the layers were jointly trained. As we continue to the right, we see that layer 6 is nearly back to the base level of performance, as is layer 7. As we get closer and closer to the final 500-way softmax output layer (8), there is less to relearn, and apparently relearning these one or two layers is simple enough for gradient descent to find a good solution. Alternately, we may say that there is less co-adaptation of features between layers 6 and 7 or between 7 and 8.

We are not sure whether or not this effect has been previously observed in the literature. Certainly one would suspect that optimization difficulties might occur, but we do not believe it has been previously shown that such difficulties are worse in the middle of a network than near the bottom or top.

\item The light blue \net{AnA+} points show that, as expected, when we allow the copied lower layer features to learn as well, we're able to find a solution just as good as the original solution. The whole network is trained, just initialized from a partial previous solution instead of completely randomly, which neither helps nor hurts performance.

\item The dark red \net{BnA} points show the effect we set out to measure in the first place: the transferability of features from one network to another at each layer. Layers one and two transfer almost perfectly from \net{B} to  \net{A}, giving evidence that at least for our two tasks, not only are the gabor features general, but the second layer features are as well. Layer three shows a slight drop, and layers 4-7 show a more significant drop in performance. Thanks to the \net{ANA} points, we can tell that this drop is from a combination of two separate effects: the drop from lost co-adaptation \emph{and} the drop from features which are less and less general. On layers 3, 4, and 5, the first effect dominates, whereas on layers 6 and 7 the first effect diminishes and the specificity of representation dominates the drop in performance.

Although examples of successful feature transfer have been reported elsewhere in the literature, to our knowledge these results have been limited to noticing that transfer from a given layer is much better than chance, e.g. noticing that the \net{BnA} points are much better than chance level performance (.002 for 500 classes). We believe this is the first time that the extent to which transfer is successful has been carefully quantified layer by layer and that the two separate effects have been decoupled, showing that each effect dominates in part of the regime.

\item The light red \net{BnA+} points show perhaps the most surprising effect: that transferred features followed by fine-tuning result in networks that generalize better than those trained directly on the target dataset. We suspected that this effect might be simply due to longer total training time (450k base + 450k fine-tuned for \net{BnA+} vs. 450k for \net{baseA}), but this cannot be the case, because the \net{AnA+} networks are also trained for the same longer length of time and do not exhibit this boost in performance.

Thus, the most likely explanation is that even after 450k iterations of fine tuning (beginning with completely random top layers), the effects of having seen the first (different) dataset still linger, boosting generalization performance. We found the fact that this effect can linger through so much retraining surprising. Further, this lingering boon to generalization seems not to depend very much on how much of the first network we keep: keeping anywhere from one to seven layers produces improved performance, with slightly better performance as we keep more layers. The average boost across layers 1 to 7 is 1.6\% over the base case, and the average if we keep at least five layers is 2.1\%.\footnote{It is somewhat strange for us to average the performance over several layers. We'd prefer to average many runs at the same layer, but each point is rather computationally expensive to obtain. The \net{BnA+} point at }

 (anywhere from 3 to 7 layers works to give an improvement of 1.8% on average).

the light red points vs. black points), but

is

any layer...

I thought this latter point could be due to something not so interesting, like the longer total training time, but
 - there is no improvement at all in the last 15% of the training for the black points, so running it twice as long would probably not help
 - the light blue points have been trained just as long as light red (450k train + 450k fine-tune).

\end{enumerate}

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}

Practical conclusions

If you don't have a big second dataset:

Results 2 and 4 imply that those wishing to transfer features from one dataset to another face not only the problem of specificity, but....

If you do have a big second dataset:

A final thing to notice is that all layers are fairly general. Even the networks in column 7, in which only the final 500-way softmax layer is retrained to the new dataset, suffer only an 8\% accuracy drop.

Caveat: We actually have to be careful here. These results only show that a random split of half of ImageNet transfers / generalizes to the other half. However, there are many related classes in the dataset. For example, here are 13 felids:

\begin{verbatim}
   n02123045 tabby, tabby cat
   n02123159 tiger cat
   n02123394 Persian cat
   n02123597 Siamese cat, Siamese
   n02124075 Egyptian cat
   n02125311 cougar, puma, catamount, mountain lion, Felis concolor
   n02127052 lynx, catamount
   n02128385 leopard, Panthera pardus
   n02128757 snow leopard, ounce, Panthera uncia
   n02128925 jaguar, panther, Panthera onca, Felis onca
   n02129165 lion, king of beasts, Panthera leo
   n02129604 tiger, Panthera tigris
   n02130308 cheetah, chetah, Acinonyx jubatus
\end{verbatim}

Because each A/B half will probably contain 6 or 7 of these, each half will have detectors trained on all levels to classify some types of felids. When generalizing to the other half, we would expect that the new high-level felid detectors trained on top of fixed old low-level felid detectors would work well. With this in mind, I've made a special manual 449-class vs 515-class split of the dataset into "natural" and "man made" categories to show how mid-level features do or do not transfer across this larger generalization gap (experiments still running).

Part 2 of results:

There's a little detail of the plot in the first email that bugged me. I expected monotonic performance drop as we move to the right on the plot, that is, as we copy more and more layers from the wrong dataset, accuracy should decrease.

However, if you look at layers 5 and 6, you'll notice that transfer performance when the first 5 layers are trained on A and the rest are trained on B is actually slightly *worse* than when we copy the first 6 layers. It's better to copy an extra layer of filters learned from the wrong dataset. It's just a tiny bump, but why?

It turns out, I think, that the bump is due to some interesting optimization difficulties. To expose them, I repeated the transfer experiments, but this time transferred the A filters to a new network and then retrained it on A. Concretely:
 - train baseA on A
 - copy the first N layers of baseA to a new network transferANA and freeze them
 - randomly initialize the higher layers of transferANA and train only those layers toward A

(Note: we could have just done this on the whole dataset, not the A half, but then any observed effects would have been confounded with effects due to differing dataset size)

This process gives the following results (blue dots show the performance of transferANA for various N)

+-------------+
|                    |
|                    |
+-------------+
(((( Figure 2 with blue and red dots ))))

Conclusions (from red and blue points):

 - Now we can reinterpret the red points as dropping from maximum performance for two separate reasons: optimization difficulties (drop in blue curve) and dataset mismatch (gap between blue and red). The gap between blue and red shows the dataset mismatch portion of the performance drop, and it's monotonically getting larger, as initially expected. It's just tricky to measure on its own.

Conclusions (just from blue points):

 - If we chop the network in half in the early layers (1,2,3) and retrain the upper part of it, gradient descent is able to find as good a solution as if the whole network is trained from scratch (expected).

 - Similarly for chopping the network at the upper layers (6,7) (expected).

 - However, if we chop the network after layer 4 or 5, gradient descent cannot recover as good of a solution as was found initially when everything was randomized. This seems to point toward a type of coadaptation of units across layers that can only be found when the units are trained together.

Is this later point surprising? It was to me. Has this effect been observed elsewhere?

\subsection{Control Experiment -- random filters}

((do this later... maybe put at end of Exchange section instead? ))

Compare to Jarret 2009 (first two layers don't work great...)
\cite{Jarrett-ICCV2009}

\section{Conclusions}

\edit{write this}

### 2014-06-06 paper/plots/make_cropped.sh

@@ -1,0 +1,4 @@
+#! /bin/bash
+
+pdfcrop result_transfer_lines.pdf result_transfer_lines_crop.pdf
+pdfcrop result_transfer.pdf result_transfer_crop.pdf

### 2014-06-06 paper/body.tex
more writing; trimmed down bib files

@@
 \begin{itemize}
-\item A \emph{selffer} network \net{B3B+} just like \net{B3B}, but where all layers learn
-\item A \emph{transfer} network \net{A3B+} just like \net{A3B}, but where all layers learn
+\item A \emph{selffer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
+\item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn
 \end{itemize}
@@
 Similarly, we've aggregated the \net{BnA} and \net{AnB} networks and just call them \net{BnA}}, that is, a network that was trained on dataset \dA, chopped off at layer $n$, and then whose upper layers were reinitialized and retrained toward dataset \dA while the lower layers remained frozen.
-The light blue points represent \net{AnA+} networks, the same as \net{AnA} but where the lower layers were trained as well.
+The light blue points represent \net{AnA^+} networks, the same as \net{AnA} but where the lower layers were trained as well.
 Each dark red dot represents a \net{BnA} network, one whose first $n$ layers are copied from \net{baseB} and frozen, and then whose upper layers were randomly initialized and trained toward dataset \dA.
-The light red points represent \net{BnA+} networks where all layers were fine-tuned.
+The light red points represent \net{BnA^+} networks where all layers were fine-tuned.
 
@@
 
-\item The light blue \net{AnA+} points show that, as expected, when we allow the copied lower layer features to learn as well, we're able to find a solution just as good as the original solution.
+\item The light blue \net{AnA^+} points show that, as expected, when we allow the copied lower layer features to learn as well, we're able to find a solution just as good as the original solution.
 The whole network is trained, just initialized from a partial previous solution instead of completely randomly, which neither helps nor hurts performance.
@@
 
-\item The light red \net{BnA+} points show perhaps the most surprising effect: that transferred features followed by fine-tuning result in networks that generalize better than those trained directly on the target dataset.
-We suspected that this effect might be simply due to longer total training time (450k base + 450k fine-tuned for \net{BnA+} vs.
-450k for \net{baseA}), but this cannot be the case, because the \net{AnA+} networks are also trained for the same longer length of time and do not exhibit this boost in performance.
+\item The light red \net{BnA^+} points show perhaps the most surprising effect: that transferred features followed by fine-tuning result in networks that generalize better than those trained directly on the target dataset.
+We suspected that this effect might be simply due to longer total training time (450k base + 450k fine-tuned for \net{BnA^+} vs.
+450k for \net{baseA}), but this cannot be the case, because the \net{AnA^+} networks are also trained for the same longer length of time and do not exhibit this boost in performance.
 
-Thus, the most likely explanation is that even after 450k iterations of fine tuning (beginning with completely random top layers), the effects of having seen the first (different) dataset still linger, boosting generalization performance.
+Thus, the most likely explanation is that even after 450k iterations of fine tuning (beginning with completely random top layers), the effects of having seen the alternate dataset still linger, boosting generalization performance.
 We found the fact that this effect can linger through so much retraining surprising.
-Further, this lingering boon to generalization seems not to depend very much on how much of the first network we keep: keeping anywhere from one to seven layers produces improved performance, with slightly better performance as we keep more layers.
-The average boost across layers 1 to 7 is 1.6\% over the base case, and the average if we keep at least five layers is 2.1\%.\footnote{It is somewhat strange for us to average the performance over several layers.
-We'd prefer to average many runs at the same layer, but each point is rather computationally expensive to obtain.
-The \net{BnA+} point at }
-
- (anywhere from 3 to 7 layers works to give an improvement of 1.8% on average).
-
-the light red points vs. black points), but
-
-is
-
-any layer...
-
-I thought this latter point could be due to something not so interesting, like the longer total training time, but
- - there is no improvement at all in the last 15% of the training for the black points, so running it twice as long would probably not help
- - the light blue points have been trained just as long as light red (450k train + 450k fine-tune).
+Further, this lingering boon to generalization seems not to depend very much on how much of the first network we keep to initialize the second network: keeping anywhere from one to seven layers produces improved performance, with slightly better performance as we keep more layers.
+The average boost across layers 1 to 7 is 1.6\% over the base case, and the average if we keep at least five layers is 2.1\%.\footnote{It is somewhat strange for us to aggregate the performance over several layers.
+Indeed, we'd prefer to average many runs at the same layer, but each point is rather computationally expensive to obtain so we have very few as of the time of this submission.
+However, we think some aggregation is informative, because the performance at each layer is based on completely different random draws of initialization weights.
+Thus, the fact that layers 5, 6, and 7 result in almost identical performance across random draws is at least somewhat indicative that multiple runs at a given layer would result in similar performance.} The degree of performance boost is shown in Table~\ref{tab:boost}.
 
@@
 
+% Computed like this (set LAYER = {1,3,5})
+%
+% LAYER = 1
+% nested = [list(mb_selffer_ft[ii]['valid_top1_acc']) for ii in range(LAYER,8)]
+% case_selffer = array([item for sublist in nested for item in sublist])
+% 
+% nested = [list(mb_transfer_ft[ii]['valid_top1_acc']) for ii in range(LAYER,8)]
+% case_transfer = array([item for sublist in nested for item in sublist])
+% 
+% print 'transfer - selffer', case_transfer.mean() - case_selffer.mean()
+% print 'transfer - base',    case_transfer.mean() - case_base.mean()
+% 
+% #print stats.ttest_rel(case_base, case_selffer)
+% print 'base    vs selffer ', stats.ttest_ind(case_base, case_selffer)
+% #print stats.ttest_rel(case_base, case_transfer)
+% print 'base    vs transfer', stats.ttest_ind(case_base, case_transfer)
+% print 'selffer vs transfer', stats.ttest_ind(case_selffer, case_transfer)
+
 \begin{table}[t]
-\caption{Convolutional Network architecture sizes and hyperparameters}
-\label{tab:network_architecture}
+\caption{Performance accuracy boost of transfer + fine-tuning \net{BnA^+} over controls. All differences are significant at the $p < .001$ level.}
+\label{tab:boost}
 \begin{center}
-\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
+\begin{tabular}{|c|c|c|}
 \hline
-       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
-name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
+           & mean boost  & mean boost \\
+layers     & over        & over \\
+aggregated & \net{baseA} & selffer \net{AnA^+} \\
 \hline
-conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
-conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
-conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
-conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
-conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
-fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
-fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
-fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
+1-7        & 1.6\%       & 1.4\% \\
+3-7        & 1.8\%       & 1.4\% \\
+5-7        & 2.1\%       & 1.7\% \\
 \hline
@@
 \end{table}
+
+\section{Conclusions}
 

### 2014-06-06 paper/abstract.tex
added todo command

% !TEX root = main.tex

\edit{write this abstract}

### 2014-06-06 paper/body.tex
added todo command

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% !TEX root = main.tex
 
@@
 
-Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}).
+Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}) \editbox{fix broken figure ref here}.
 This happens with such frequency that not only is it no longer surprising, but to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a bug somewhere in one's code.
@@
 \caption{\edit{Caption here...}}
-\label{fig:transfer}
+\label{i}
 \end{figure}
@@
 \begin{table}[t]
-\caption{Convolutional Network architecture sizes and hyperparameters}
+\caption{Convolutional Network architecture sizes and hyperparameters. \todo{explain what R vs. S is}}
 \label{tab:network_architecture}

### 2014-06-06 paper/plots/make_cropped.sh
Added a fig

@@ -2,3 +2,4 @@
 
 pdfcrop result_transfer_lines.pdf result_transfer_lines_crop.pdf
 pdfcrop result_transfer.pdf result_transfer_crop.pdf
+pdfcrop result_random_nm_combined.pdf result_random_nm_combined_crop.pdf

### 2014-06-06 paper/body.tex
Added a fig
working on figure caption

@@
 \end{center}
-\caption{\edit{Caption here...}}
+\caption{Overview of the experimental treatments and controls.
+\emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \todo{cite}.
+Training occurs on only half the dataset (labels A) for consistency with the experimental treatments.
+The baseline control is repeated for each half of the dataset (labels A and labels B).
+\emph{Third row:} }
 \label{i}

### 2014-06-06 paper/body.tex
finished draft of caption for figure 1

--- 2014-06-06 paper/body.tex
@@
 \end{center}
-\caption{\edit{Caption here...}}
+\caption{Overview of the experimental treatments and controls.
+\emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \citep{Krizhevsky-2012}.
+Training occurs on only half the dataset (e.g.
+dataset A) for consistency with the experimental treatments.
+The baseline control is repeated for each half of the dataset (A and B).
+The labeled rectangles (e.g.
+$W_{A1}$) represent the weight vector for that layer.
+That the rectangle is colored indicates that the weight layer has been trained on the dataset of that color (e.g.
+dataset A).
+The vertical, ellipsoidal bars represent neural activations that occur when the network is activated.
+\emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern).
+The weights of the first $N$ layers of the network are locked, meaning they do not change during training.
+The remaining layers are trained as normal on half the dataset.
+A replicate (not pictured) is performed on the other half of the dataset.
+\emph{Fourth row:} The ``selfer network'' control.
+In this control the first $N$ weight layers of the network are copied from a base network (e.g.
+one trained on dataset B) and then the entire network is trained on that same dataset (in this example, dataset B).
+These layers are either locked during training (in the ``locked selfer treatments'') or allowed to train as usual (in the ``released selfer treatments''.
+The weights of layers after the first $N$ layers are initialized randomly and then allowed to train as usual.
+This treatment tests whether filters at different layers need to co-adapt during training, or if they can be trained asynchronously.
+\emph{Fifth row:} The ``transfer network'' experimental treatment.
+Same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.
+B) and then the entire network is trained on the \emph{other} half of the dataset (e.g.
+dataset A).
+This treatment tests transfer learning.}
 \label{i}

### 2014-06-06 paper/body.tex
table caption edits

@@
 \begin{table}[t]
-\caption{Convolutional Network architecture sizes and hyperparameters. \todo{explain what R vs. S is}}
+\caption{Convolutional Network architecture sizes and hyperparameters.
+Conv stands for Convolutional layers.
+FC stands for fully-connected layers.
+R/S indicates that the layer consists of rectilinear or sigmoidal neurons.
+Neurons in dropout layers fail to fire with 50\% probability \todo{accurate?} \citep{Hinton-et-al-arxiv2012}\todo{Do we need to explain what groups means?
+Stride?} LRN stands for local response normalization \citep{Krizhevsky-2012}.}
 \label{tab:network_architecture}
@@
 \begin{table}[t]
-\caption{Parameter initializations and learning rates}
+\caption{Parameter initializations and learning rates. \todo{JY: I expanded the table headings (we have the space). Please check that I did so accurately. I had to guess on most.}}
 \label{tab:learning_hyperparams}
@@
 \cline{2-7}
-       & gaus   & LR-mult & decay &  const  & LR  & decay \\
+       & Gaussian Std. Dev.   & Local Response-multiplier & decay &  const  & Local Response  & decay \\
 \hline

### 2014-06-06 paper/abstract.tex
edits from jason and yoshua

@@
 \edit{write this abstract}
+
+...
+
+We make the first comparison because \cite{Jarrett-ICCV2009} showed, --- quite strikingly --- that the combination of random convolutional features,  rectification, pooling, and local normalization can work almost as well as learned features.
+They showed this on relatively small networks
+
+Our results from layers 1 and 2 suggest that getting random features to work well may not be as straightforward as they found.
+We use max pooling and local normalization on layers 1 and 2 just as they did, but we use relu(x) where they used abs(tanh(x)).
+The difference in performance could be due to a few factors: slightly different nonlinearity, the dataset itself, sizes of critical pieces of the network, etc.

### 2014-06-06 paper/body.tex
edits from jason and yoshua

--- 2014-06-06 paper/body.tex
@@
 
-\section{Defining Generality vs. Specificity}
+\section{Generality vs. Specificity as transfer from one dataset to another}
 \label{sec:definition}
@@
 Each image in the training and validation sets is labeled with one of 1000 classes.
+
 To create tasks \dA and \dB, we randomly split the 1000 classes into two groups, \dA and \dB, each containing 500 classes and approximately half of the data, or about 645,000 examples each.
@@
 This treatment tests transfer learning.}
-\label{i}
+\label{fig:transfer}
 \end{figure}
 
-\section{Details of Experiment}
+The results for the random \dA/\dB splits are shown in Section~\ref{sec:experiments_ab}.
+Before proceeding, we note an important point about the random splits chosen in this way.
+ImageNet contains 1000 classes, some of which occur in clusters of related classes.
+For example, there happen to be many types of certain animals included in the dataset, particularly dogs and cats, like these 13 classes from the biological family \emph{Felidae}:
+
+{
+\small
+\begin{verbatim}
+   ID        Description
+   n02123045 tabby, tabby cat
+   n02123159 tiger cat
+   n02123394 Persian cat
+   n02123597 Siamese cat, Siamese
+   n02124075 Egyptian cat
+   n02125311 cougar, puma, catamount, mountain lion, Felis concolor
+   n02127052 lynx, catamount
+   n02128385 leopard, Panthera pardus
+   n02128757 snow leopard, ounce, Panthera uncia
+   n02128925 jaguar, panther, Panthera onca, Felis onca
+   n02129165 lion, king of beasts, Panthera leo
+   n02129604 tiger, Panthera tigris
+   n02130308 cheetah, chetah, Acinonyx jubatus
+\end{verbatim}
+}
+
+Because each randomly chosen \dA/\dB half will probably contain 6 or 7 of these felids, each half will have detectors trained on all levels to classify some types of felids.
+When generalizing to the other half, we would expect that the new high-level felid detectors trained on top of fixed old low-level felid detectors would work well.
+
+For comparison, we've also created a special split of the dataset into two halves that are as far apart from each other as possible: one category containing only \emph{natural} classes and another containing \emph{man-made} objects.
+This split is not quite even --- there are 449 classes in the natural group and 551 in the man-made group.
+In Section~\ref{sec:experiments_random_nm} we show (a) how features transfer more poorly (so we say the are more specific) across this larger generalization gap and (b) how the generality of subsequent layers falls of smoothly.
+
+\edit{mention faster training here}
+
+\section{Details of Experimental Setup}
 
 Since \cite{Krizhevsky-2012} won the ImageNet 2012 competition, there has naturally been much interest and work toward tweaking hyperparameters of large convolutional models.
-For example, \cite{Zeiler+et+al-arxiv2013b} found that it is better to decrease the first layer filters sizes from $11x11$ to $7x7$ and to use a smaller stride of $2$ instead of $4$.
+For example, \cite{Zeiler+et+al-arxiv2013b} found that it is better to decrease the first layer filters sizes from $11\times 11$ to $7\times 7$ and to use a smaller stride of $2$ instead of $4$.
 When beginning this study we faced the decision of exactly which convolutional architecture to use for our experiments.
@@
 
-To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \cite{donahue+jia-2013-arxiv}.
-We followed \cite{donahue+jia-2013-arxiv} in making a few minor departures from \cite{Krizhevsky-2012}: we skip the data augmentation trick of adding random multiples of principle components of pixel RGB values, which produced only a $1\%$ improvement in the original paper, and we warped images to $256x256$ instead of scaling to keep the aspect ratio and then cropping.
+To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \citep{donahue+jia-2013-arxiv}.
+We followed \citet{donahue+jia-2013-arxiv} in making a few minor departures from \cite{Krizhevsky-2012}: we skip the data augmentation trick of adding random multiples of principle components of pixel RGB values, which produced only a $1\%$ improvement in the original paper, and we warped images to $256\times 256$ instead of scaling to keep the aspect ratio and then cropping.
 In another difference, we placed the Local Response Normalization layers just \emph{after} the pooling layers, instead of before them.
@@
 These selections were made after looking at the learning curves for the base case and estimating at which points in each region of constant learning rate the learning had plateaued and thus annealing could take place.
-A typical learning curve is shown in Figure~\ref{typical_learning}.
+\edit{A typical learning curve is shown in Figure~\ref{typical_learning}.}
 
@@
 
+As mentioned earlier, we did two sets of experiments.
+The main experiment using random random \dA/\dB splits is discussed in Section~\ref{sec:experiments_ab}, and the two comparison cases using random filters and the Natural/Man-made split is presented in Section~\ref{sec:experiments_random_nm}.
+
+\subsection{Random \dA/\dB splits}
+\label{sec:experiments_ab}
+
 \begin{figure}[htpb]
@@
 Similarly, we've aggregated the \net{BnA} and \net{AnB} networks and just call them \net{BnA}}, that is, a network that was trained on dataset \dA, chopped off at layer $n$, and then whose upper layers were reinitialized and retrained toward dataset \dA while the lower layers remained frozen.
-The light blue points represent \net{AnA^+} networks, the same as \net{AnA} but where the lower layers were trained as well.
+The light blue points represent \net{AnA^+} networks, the same as \net{AnA} but where the lower layers were fine-tuned as well.
 Each dark red dot represents a \net{BnA} network, one whose first $n$ layers are copied from \net{baseB} and frozen, and then whose upper layers were randomly initialized and trained toward dataset \dA.
@@
 \item The black \net{baseA} points show that the mean performance of a network simply trained to classify a random subset of 500 classes attains a top-1 accuracy of 0.625, or 37.5\% top-1 error.
-This is different than the 42.5\% top-1 error attained on the 1000 class network for two a combination of two reasons: it is pushed higher because the network is trained only on half of the data, which could lead to more overfit, and it is pushed lower because there are only 500 classes, so there are only half as many ways to make mistakes.
+This is different than the 42.5\% top-1 error attained on the 1000 class network for a combination of two reasons: it is pushed higher because the network is trained only on half of the data, which could lead to more overfit, and it is pushed lower because there are only 500 classes, so there are only half as many ways to make mistakes.
 It is this latter effect that dominates, leading to lower error overall.
@@
 Thus, the most likely explanation is that even after 450k iterations of fine tuning (beginning with completely random top layers), the effects of having seen the alternate dataset still linger, boosting generalization performance.
-We found the fact that this effect can linger through so much retraining surprising.
+We found surprising the fact that this effect can linger through so much retraining.
 Further, this lingering boon to generalization seems not to depend very much on how much of the first network we keep to initialize the second network: keeping anywhere from one to seven layers produces improved performance, with slightly better performance as we keep more layers.
@@
 
+\subsection{Random filters and Natural/Man-made split}
+\label{sec:experiments_random_nm}
+
+In this section we compare the transfer performance of our random \dA/\dB splits to a control --- completely random filters --- and to our manually created 449 vs. 551 class natural/man-made split.
+
+We make the first comparison because \cite{Jarrett-ICCV2009} showed, --- quite strikingly --- that the combination of random convolutional features, rectification, pooling, and local normalization can work almost as well as learned features.
+They showed this on relatively small networks of two or three learned layers and on a smaller dataset; and it is natural to ask whether or not the nearly optimal performance of random filters carries over to a deeper network trained on a larger dataset.
+
+We make the second comparison to see how features transfer between two tasks that are as far apart as possible using the ImageNet dataset.
+Many are using and will use features trained from ImageNet for completely new tasks, and this second control gives some idea of how well features from various layers will transfer.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=1\linewidth]{plots/result_random_nm_combined_crop.pdf}
+\end{center}
+\caption{\edit{Caption here...}}
+\label{fig:random_and_nm}
+\end{figure}
+
+Figure~\ref{fig:random_and_nm} shows the results of these two additional experiments.
+The upper-left subplot shows the accuracy obtained when using random filters for the first $n$ layers, for various choices of $n$.
+Performance falls off fairly quickly in layers 1 and 2, which suggests that getting random features to work in general convnets may not be as straightforward as it was for the smaller network size and smaller dataset used by \cite{Jarrett-ICCV2009}.
+However, the comparison is a bit tricky, because whereas we use max pooling and local normalization on layers 1 and 2 just as they did, we use a different nonlinearity: $\mathrm{relu}(x)$ instead of $\mathrm{abs}(\mathrm{tanh}(x))$.
+The difference in performance could be due to a few factors: slightly different nonlinearity, the dataset itself, sizes of critical pieces of the network, etc.
+Their experiment only considered two layers of random features.
+In our case and with our chosen hyperparameters, we see that by the third layer of random features, accuracy has dropped nearly to the chance level.
+Of course, this represents only one datapoint, and it may well be possible to tweak layer sizes and random initialization magnitudes to enable much better performance.
+
+The upper-right subplot of Figure~\ref{fig:random_and_nm} shows the accuracy of the \net{baseA} (black circle), \net{baseB} (black square), \net{BnA} (magenta circles), and \net{AnB} (magenta squares) networks.
+The \net{baseA} and \net{BnA} networks are both eventually trained toward \dA, which is the natural half of the split and has higher average performance.
+This may be due to having only 449 classes instead of 551, or simply being an easier task, or both.
+
+Finally, in the bottom plot of Figure~\ref{fig:random_and_nm} we normalize these several experiments by subtracting the performance of their individual base cases (which vary from each other for reasons mentioned above).
+We then plot the relative drop in performance as we use more random layers or pull more layers from a network trained on another dataset.
+This comparison makes two things apparent: first, that the transferability gap between two randomly selected \dA and \dB halves grows more slowly with increasing layer than does the transferability gap between two less related halves, and second, that for this network architecture, transferring even from a distant task is better than just using random filters.
+This latter result may hold because the networks trained in \citep{Jarrett-ICCV2009} could have been well into the overfitting regime on a dataset as small as Caltech-101 \citep{Fei-Fei.2004}.
+
 \section{Conclusions}
@@
 A final thing to notice is that all layers are fairly general.
-Even the networks in column 7, in which only the final 500-way softmax layer is retrained to the new dataset, suffer only an 8\% accuracy drop.
-
-Caveat: We actually have to be careful here.
-These results only show that a random split of half of ImageNet transfers / generalizes to the other half.
-However, there are many related classes in the dataset.
-For example, here are 13 felids:
-
-\begin{verbatim}
-   n02123045 tabby, tabby cat
-   n02123159 tiger cat
-   n02123394 Persian cat
-   n02123597 Siamese cat, Siamese
-   n02124075 Egyptian cat
-   n02125311 cougar, puma, catamount, mountain lion, Felis concolor
-   n02127052 lynx, catamount
-   n02128385 leopard, Panthera pardus
-   n02128757 snow leopard, ounce, Panthera uncia
-   n02128925 jaguar, panther, Panthera onca, Felis onca
-   n02129165 lion, king of beasts, Panthera leo
-   n02129604 tiger, Panthera tigris
-   n02130308 cheetah, chetah, Acinonyx jubatus
-\end{verbatim}
-
-Because each A/B half will probably contain 6 or 7 of these, each half will have detectors trained on all levels to classify some types of felids.
-When generalizing to the other half, we would expect that the new high-level felid detectors trained on top of fixed old low-level felid detectors would work well.
-With this in mind, I've made a special manual 449-class vs 515-class split of the dataset into "natural" and "man made" categories to show how mid-level features do or do not transfer across this larger generalization gap (experiments still running).
-
-Part 2 of results:
-
-There's a little detail of the plot in the first email that bugged me.
-I expected monotonic performance drop as we move to the right on the plot, that is, as we copy more and more layers from the wrong dataset, accuracy should decrease.
-
-However, if you look at layers 5 and 6, you'll notice that transfer performance when the first 5 layers are trained on A and the rest are trained on B is actually slightly *worse* than when we copy the first 6 layers.
-It's better to copy an extra layer of filters learned from the wrong dataset.
-It's just a tiny bump, but why?
-
-It turns out, I think, that the bump is due to some interesting optimization difficulties.
-To expose them, I repeated the transfer experiments, but this time transferred the A filters to a new network and then retrained it on A.
-Concretely:
- - train baseA on A
- - copy the first N layers of baseA to a new network transferANA and freeze them
- - randomly initialize the higher layers of transferANA and train only those layers toward A
-
-(Note: we could have just done this on the whole dataset, not the A half, but then any observed effects would have been confounded with effects due to differing dataset size)
-
-This process gives the following results (blue dots show the performance of transferANA for various N)
-
-+-------------+
-|                    |
-|                    |
-+-------------+
-(((( Figure 2 with blue and red dots ))))
-
-Conclusions (from red and blue points):
-
- - Now we can reinterpret the red points as dropping from maximum performance for two separate reasons: optimization difficulties (drop in blue curve) and dataset mismatch (gap between blue and red).
-The gap between blue and red shows the dataset mismatch portion of the performance drop, and it's monotonically getting larger, as initially expected.
-It's just tricky to measure on its own.
-
-Conclusions (just from blue points):
-
- - If we chop the network in half in the early layers (1,2,3) and retrain the upper part of it, gradient descent is able to find as good a solution as if the whole network is trained from scratch (expected).
-
- - Similarly for chopping the network at the upper layers (6,7) (expected).
-
- - However, if we chop the network after layer 4 or 5, gradient descent cannot recover as good of a solution as was found initially when everything was randomized.
-This seems to point toward a type of coadaptation of units across layers that can only be found when the units are trained together.
-
-Is this later point surprising? It was to me. Has this effect been observed elsewhere?
-
-\subsection{Control Experiment -- random filters}
-
-((do this later... maybe put at end of Exchange section instead? ))
-
-Compare to Jarret 2009 (first two layers don't work great...)
-\cite{Jarrett-ICCV2009}
-
-\section{Conclusions}
-
-\edit{write this}
+Even the networks in column 7, in which only the final 500-way softmax layer is retrained to the new dataset, suffer only an 8\% accuracy drop in the A/B split case, but a much larger 25\% drop in the natural/manmade case.
+In the natural/man-made split case, the drop is fairly smooth through the network

### 2014-06-06 paper/body.tex
minimum necessary figure caption
writing edits

@@
 
-(((( two gabor features from very different networks ))))
+(((( two Gabor features from very different networks ))))
 
@@
 
-Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}) \editbox{fix broken figure ref here}.
-This happens with such frequency that not only is it no longer surprising, but to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a bug somewhere in one's code.
-In fact, this paper's authors are now used to checking for gabor features in the first layer simply to assure ourselves that the training is at least partially working.
+Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble Gabor filters in the first layer (see Figure~\ref{fig:layer1}) \todo{fix broken figure ref here}.
+The appearance of these Gabor filters is so common that to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a software bug.
+%In fact, this paper's authors are now used to checking for Gabor features in the first layer simply to assure ourselves that the training is at least partially working.
 
-Because finding gabor features on the first layer seems to occur regardless of the exact cost function and natural image dataset used, we may call these these features \emph{general}.
+Because finding Gabor features on the first layer seems to occur regardless of the exact cost function and natural image dataset used, we may call these these features \emph{general}.
 On the other hand, we know that the last layer of a trained network will depend greatly on the chosen \{network model, dataset\} combination.
@@
 In this sense, let's say that the last layer features are \emph{specific}.
-So far these terms are only intuitively defined, but we shall give one possible more rigorous definition soon.
+So far these terms are only intuitively defined, but we shall provide a candidate for a more rigorous definition below.
+\todo{Consider something like: ``Empirically, we know that these filter are generic because they can be transferred to other networks and perform well [cites].
+Transferring information learned on one task or dataset to a new task or data set is know as \emph{Transfer Learning} [cites].''}
 
-If the layer 1 features are general, and the last layer features are specific, we know that somewhere in the network there must be a transition from general to specific.
+If these Gabor features of the first features are general, and the features of the last layer are specific, there must be a transition from general to specific somewhere in the network.
 This observation raises a few questions:
@@
 
-We have noted the curious tendency of gabor features to show up in the first layer of neural networks trained on natural images for a large range of network architectures and cost functions.
+We have noted the curious tendency of Gabor features to show up in the first layer of neural networks trained on natural images for a large range of network architectures and cost functions.
 We say these features are general if they are useful for many different tasks or specific if they are useful only for a few.
@@
 \end{center}
-\caption{\edit{Caption here...}}
+\caption{Accuracy of each treatment and control.
+\emph{Top panel:} Raw data.
+\emph{Bottom panel}: Lines connect the medians of each treatment.
+Shaded areas and text highlight key takeaway messages.
+\todo{This is the min.
+required if we explain the figure in the main text.}
+}
 \label{fig:results}
@@
 We can see at layer one that the performance is the same (as the \net{baseA} points), which was expected.
-If we learn eight layers of features, save the first layer of learned gabor features, and reinitialize the whole network and retrain it toward the same task, we'd expect to do just as well.
+If we learn eight layers of features, save the first layer of learned Gabor features, and reinitialize the whole network and retrain it toward the same task, we'd expect to do just as well.
 This is also true for layer 2.
@@
 \item The dark red \net{BnA} points show the effect we set out to measure in the first place: the transferability of features from one network to another at each layer.
-Layers one and two transfer almost perfectly from \net{B} to  \net{A}, giving evidence that at least for our two tasks, not only are the gabor features general, but the second layer features are as well.
+Layers one and two transfer almost perfectly from \net{B} to  \net{A}, giving evidence that at least for our two tasks, not only are the Gabor features general, but the second layer features are as well.
 Layer three shows a slight drop, and layers 4-7 show a more significant drop in performance.

### 2014-06-06 paper/body.tex
small change

@@
 So far these terms are only intuitively defined, but we shall provide a candidate for a more rigorous definition below.
-\todo{Consider something like: ``Empirically, we know that these filter are generic because they can be transferred to other networks and perform well [cites].
-Transferring information learned on one task or dataset to a new task or data set is know as \emph{Transfer Learning} [cites].''}
-
 If these Gabor features of the first features are general, and the features of the last layer are specific, there must be a transition from general to specific somewhere in the network.
@@
 	\item Can we quantify the degree to which a particular layer is general or specific?
-	\item For a particular deep network, does the transition occur suddenly from layer $n$ to $n+1$, or is it spread out over several layers?
+	\item For a particular deep network, does the transition occur suddenly at a single layer, or is it spread out over several layers?
 	\item Where does this transition take place: near the bottom, middle, or top of the network?
@@
 
-Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task.
+Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \todo{cites}.
 The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task.

### 2014-06-06 paper/abstract.tex
title, abstract, and conclusion

--- 2014-06-06 paper/abstract.tex
@@
 
-\edit{write this abstract}
+A high percentage of recently reported deep networks trained on
+natural images exhibit a curious aspect in common: they all learn
+features similar to gabor filters on the first layer. Such features
+appear to be \emph{general}, as opposed to \emph{specific} for a
+particular task. Because higher layers are difficult to visualize, not
+as much is known about whether the are general or specific. In this
+paper we experimentally quantify the generality of neurons on each
+layer of a deep convolutional neural network and through this expose a
+few surprising aspects. First, we find that transferability is
+negatively affected by two distinct issues --- not only the expected
+specialization of higher layer neurons to their original task at the
+expense of the target task, but also optimization difficulties related
+to splitting networks in the middle of co-adapted neurons. In an
+example network trained on ImageNet, we demonstrate that either of
+these two issues may dominate, depending on whether features are
+transferred from the bottom, middle, or top of the network.  We also
+show how the transferability gap grows as the distance between base
+task and target task increases, but how even transfer from distant
+tasks can be better than using random features. Finally, we show a
+surprising result that initializing a network with transferred
+features from almost any number of layers can produce a boost to
+generalization that lingers even after fine-tuning to the target
+dataset.

### 2014-06-06 paper/body.tex
title, abstract, and conclusion

--- 2014-06-06 paper/body.tex
@@
 
-Practical conclusions
-
-If you don't have a big second dataset:
-
-Results 2 and 4 imply that those wishing to transfer features from one dataset to another face not only the problem of specificity, but....
-
-If you do have a big second dataset:
-
-A final thing to notice is that all layers are fairly general.
-Even the networks in column 7, in which only the final 500-way softmax layer is retrained to the new dataset, suffer only an 8\% accuracy drop in the A/B split case, but a much larger 25\% drop in the natural/manmade case.
-In the natural/man-made split case, the drop is fairly smooth through the network
+In this paper we've demonstrated a method for quantifying the ability to transfer features from a deep net layer by layer.
+We showed how transferability is negatively affected by two distinct issues --- optimization difficulties related to splitting networks in the middle of co-adapted layers and the specialization of higher layer neurons to their original task at the expense of the target task.
+In a large convolutional network similar to those that represent the state of the art on the large ImageNet dataset, we observed that either of these two issues may dominate, depending on whether features are transferred from the bottom, middle, or top of this deep network.
+We've quantified how the transferability gap grows as the distance between tasks increases, but how even features transferred from distant tasks can be better than random features.
+Finally, we've observed that initializing a network with transferred features from almost any number of layers can produce a boost to generalization that lingers even after a lengthy training procedure.

### 2014-06-06 paper/body.tex
small change

--- 2014-06-06 paper/body.tex
@@
 The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task.
-When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen.
+When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen or ``locked'', meaning that they do not change during training on the new task.
 In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen.
 On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task.
-Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch.
+Of course, if the second dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch.
 These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.

### 2014-06-06 paper/abstract.tex
small change

@@
 
-A high percentage of recently reported deep networks trained on
+A high percentage of deep neural networks trained on
 natural images exhibit a curious aspect in common: they all learn
-features similar to gabor filters on the first layer. Such features
+features similar to Gabor filters on the first layer. Such features
 appear to be \emph{general}, as opposed to \emph{specific} for a

### 2014-06-06 paper/body.tex
intro

--- 2014-06-06 paper/body.tex
@@
 
-It has recently become possible to train much larger artificial neural networks than ever before.
-
-\editbox{write some intro fluff here vvvv}
-
-Recent progress, enabled by Convnets \cite{LeCun89}
-
-these new large networks are breaking previous performance records handily. Also unsupervised work: \cite{Le-2011-ICA} trained large unsupervised network using...
-
-Most of these use combinations of learned convolutional features, pooling over fixed local regions, and normalization of responses based on the responses of other units in the same layer (a basic form of inhibition or local competition, which has a similar effect to ``explaining away'')
-
-(speculation) It is interesting to think that, while we previously fought in a regime where mostly we tried to push performance, and most small performance gains well understood -- that is, the field of machine learning was largely a art of synthesizing functions that worked better and better -- we may soon be entering an era of the field where we have things that are so large and work so well that the performance will outpace our understanding.
-This will push the  field into a decidedly different regime, one of almost observational science where we merely poke things that work magically well to slowly remove their mystique.
-
-Grand speculation aside, here we seek to understand a few properties of one of the larger class of convolutional neural networks trained using supervised backprop.
-
-((examples))
-((diff datasets))
-((but same features!))
-
-(((( two Gabor features from very different networks ))))
-
-\editbox{write some intro fluff here ----}
-
-Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble Gabor filters in the first layer (see Figure~\ref{fig:layer1}) \todo{fix broken figure ref here}.
+Many trained neural networks reported recently in the literature exhibit a curious aspect in common: they all learn features that resemble Gabor filters in the first layer.
+% TODO: (see Figure~\ref{fig:layer1}) \todo{fix broken figure ref here}.
 The appearance of these Gabor filters is so common that to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a software bug. 
 %In fact, this paper's authors are now used to checking for Gabor features in the first layer simply to assure ourselves that the training is at least partially working.
+This phenomenon occurs not only for different datasets, but even with very different training objectives, from supervised image classification \citep{Krizhevsky-2012} to unsupervised sparse representation learning\cite{Le-2011-ICA}.
+
+% Deleted fluff
+
+%It has recently become possible to train much larger artificial neural networks than ever before. 
+%
+%\editbox{write some intro fluff here vvvv}
+%
+%Recent progress, enabled by Convnets \cite{LeCun89}
+%
+%these new large networks are breaking previous performance records handily. Also unsupervised work: \cite{Le-2011-ICA} trained large unsupervised network using...
+%
+%Most of these use combinations of learned convolutional features, pooling over fixed local regions, and normalization of responses based on the responses of other units in the same layer (a basic form of inhibition or local competition, which has a similar effect to ``explaining away'')
+%
+%(speculation) It is interesting to think that, while we previously fought in a regime where mostly we tried to push performance, and most small performance gains well understood -- that is, the field of machine learning was largely a art of synthesizing functions that worked better and better -- we may soon be entering an era of the field where we have things that are so large and work so well that the performance will outpace our understanding.
+This will push the  field into a decidedly different regime, one of almost observational science where we merely poke things that work magically well to slowly remove their mystique.
+%
+%Grand speculation aside, here we seek to understand a few properties of one of the larger class of convolutional neural networks trained using supervised backprop.
+%
+%((examples))
+%((diff datasets))
+%((but same features!))
+%
+%(((( two Gabor features from very different networks ))))
+%
+%\editbox{write some intro fluff here ----}
 
@@
 
-Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \todo{cites}.
-The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task.
-When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen.
-In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen.
-On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task.
-Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch.
-These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.
+Once one has general features from some layer of a \emph{base} network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \citep{donahue+jia-2013-arxiv}.
+The usual course is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second \emph{target} task.
+When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen, meaning that they do not change during training on the new task.
+In cases where the target dataset is smaller than the base dataset, fine-tuning the base features may result in overfitting, so the features are often left frozen.
+On the other hand, if the target dataset is large enough, the base features can be fine-tuned to the new task.
+Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch.
+We compare results from each of these two domains --- fine-tuned features or frozen features --- in a later section.
 
@@
 We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
+Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we further characterize the general to specific transition, which yields the next three results.
 \item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves.
-In different regions of the network, different effects dominate.
-\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical.
+In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
+\item We show how the transferability gap grows as the distance between base
+task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009}.
+\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
 \end{enumerate}
-
-\edit{talk a little about related work?}
-
-subsection{Related Work (no heading, just group with Intro?)}
-
-Others have loosely addressed the question of generaltiy by showing how features from layers 5/6/7 can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we're aiming for something slightly different: to observe the general to specific transition more directly, if possible.
 

### 2014-06-06 paper/abstract.tex

@@
 paper we experimentally quantify the generality of neurons on each
-layer of a deep convolutional neural network and through this expose a
-few surprising aspects. First, we find that transferability is
-negatively affected by two distinct issues --- not only the expected
-specialization of higher layer neurons to their original task at the
-expense of the target task, but also optimization difficulties related
-to splitting networks in the middle of co-adapted neurons. In an
-example network trained on ImageNet, we demonstrate that either of
-these two issues may dominate, depending on whether features are
-transferred from the bottom, middle, or top of the network.  We also
-show how the transferability gap grows as the distance between base
-task and target task increases, but how even transfer from distant
-tasks can be better than using random features. Finally, we show a
-surprising result that initializing a network with transferred
-features from almost any number of layers can produce a boost to
-generalization that lingers even after fine-tuning to the target
-dataset.
+layer of a deep convolutional neural network trained on ImageNet. The experiments also reveal a
+few unexpected insights. First, we find that transferability is
+negatively affected by two distinct issues: (a) The higher the layer, the worse it transfers.
+This result, which is to be expected, occurs because higher-level layers are more specialized to their original task, which hurts performance on the new task.
+(b) Co-adaptation occurs during training at intermediate layers such that layers must be trained at the same time to maximize performance, even on the same data set, which is a novel finding.
+%In an
+%example network , we demonstrate that either of
+%these two issues may dominate, depending on whether features are
+%transferred from the bottom, middle, or top of the network.  
+We also
+show how the benefits of transfer learning decrease as the similarity between the original task and the new task decreases, but how even transfer from dissimilar 
+tasks can be better than using random features. Finally, a
+new, surprising result is that initializing a network with transferred
+features can improve generalization, even if those features are further fine-tuned during training on a new task.

### 2014-06-06 paper/body.tex
edited caption of Fig 1 to include the new treatment names

--- 2014-06-06 paper/body.tex
@@
 \emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern).
-The weights of the first $N$ layers of the network are locked, meaning they do not change during training.
+The weights of the first $N$ layers of the network are frozen (locked), meaning they do not change during training.
 The remaining layers are trained as normal on half the dataset.
@@
 one trained on dataset B) and then the entire network is trained on that same dataset (in this example, dataset B).
-These layers are either locked during training (in the ``locked selfer treatments'') or allowed to train as usual (in the ``released selfer treatments''.
-The weights of layers after the first $N$ layers are initialized randomly and then allowed to train as usual.
+These layers are either locked during training (in the ``frozen selfer treatments'') or allowed to further fine-tune on the new data set (in the ``fine-tuned selfer treatments''), meaning that normal training occurs in those layers after initialization.
+The weights of layers after the first $N$ layers are initialized randomly and then allowed to train normally.
 This treatment tests whether filters at different layers need to co-adapt during training, or if they can be trained asynchronously.
-\emph{Fifth row:} The ``transfer network'' experimental treatment.
-Same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.
+\emph{Fifth row:} The ``transfer network'' experimental treatment is the same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.
 B) and then the entire network is trained on the \emph{other} half of the dataset (e.g.

### 2014-06-06 paper/body.tex
selffer --> selfer

@@
 \begin{itemize}
-\item A \emph{selffer} network \net{B3B} where the first $3$ layers are copied from \net{baseB} and frozen.
+\item A \emph{selfer} network \net{B3B} where the first $3$ layers are copied from \net{baseB} and frozen.
 The five higher layers are initialized randomly and trained toward dataset \dB.
@@
 \begin{itemize}
-\item A \emph{selffer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
+\item A \emph{selfer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
 \item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn
@@
 required if we explain the figure in the main text.}
+\todo{Here and in all figs, remove one f from selfer}
 }
@@
 layers     & over        & over \\
-aggregated & \net{baseA} & selffer \net{AnA^+} \\
+aggregated & \net{baseA} & selfer \net{AnA^+} \\
 \hline

### 2014-06-06 paper/body.tex
editing main contributions

@@
 The usual course is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second \emph{target} task.
-When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen, meaning that they do not change during training on the new task.
+When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left \emph{frozen}, meaning that they do not change during training on the new task.
 In cases where the target dataset is smaller than the base dataset, fine-tuning the base features may result in overfitting, so the features are often left frozen.
@@
 Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch.
-We compare results from each of these two domains --- fine-tuned features or frozen features --- in a later section.
+We compare results from each of these two techniques --- fine-tuned features or frozen features --- below.
 
@@
 \begin{enumerate}
-\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}).
-We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
-Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we further characterize the general to specific transition, which yields the next three results.
-\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves.
-In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
-\item We show how the transferability gap grows as the distance between base
-task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009}.
-\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
+\item We introduce a way to quantify the degree to which a particular layer is general or specific: how well features at a certain layer transfer from one dataset to another (Section~\ref{sec:definition}).
+We test this proposed measure on a large convnet trained on the ImageNet dataset.
+These experiments also reveal the transition from general to specific layers (Section~\ref{sec:experiments}).
+Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \citep{donahue+jia-2013-arxiv}, but here we further characterize the general to specific transition, which yields the next three results.
+\item We experimentally show two separate issues that cause performance declines from transferred features: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers, and the specificity of the features themselves.
+We show how different effects dominate at different layers of the network (Section~\ref{sec:experiments_ab}).
+\item We show how the transferability gap grows as the similarity between base
+task and target task decreases. 
+\item We compare both frozen and fine-tuning transfer to using random filters: we find that random filters do not work as well on the large ImageNet dataset as they have been reported to for smaller datasets \citep{Jarrett-ICCV2009}.
+\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better performance, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
 \end{enumerate}

### 2014-06-06 paper/body.tex
edits and cuts

--- 2014-06-06 paper/body.tex
@@
 We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
-Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we further characterize the general to specific transition, which yields the next three results.
+Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
 \item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves.
@@
 \item We show how the transferability gap grows as the distance between base
-task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009}.
+task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009} (Section~\ref{sec:experiments_random_nm}).
 \item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
@@
 We can measure the specificity of a set of features by training it on one task \dA and then using it for another task \dB.
-
-Of course, this definition depends on the distance between \dA and \dB.
-In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset.
-\edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.
-
-The dataset we use is from the ImageNet Large Scale Visual Recognition Challenge 2012 (ILSVRC2012) \citep{imagenet_cvpr09}.
-It contains 1,281,167 labeled training images and 50,000 test images.
-Each image in the training and validation sets is labeled with one of 1000 classes.
+Of course, this definition depends on the distance between \dA and \dB. In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset,
+%  \edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.
+%The dataset we use is from the
+ImageNet, as released in the Large Scale Visual Recognition Challenge 2012 (ILSVRC2012) \citep{imagenet_cvpr09}.
+It contains 1,281,167 labeled training images and 50,000 test images, and each image in the training and validation sets is labeled with one of 1000 classes.
 
@@
 
-All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{} except for the last softmax layer, which outputs 500 classes instead of 1000.
+All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{sec:setup} except for the last softmax layer, which outputs 500 classes instead of the usual 1000.
 
-We then choose an $n$ from $\{1, 2, \ldots, 7\}$ and train several networks.
+We then choose an $n$ from $\{1, 2, \ldots, 7\}$ and train and compare several networks.
 To make the discussion more concrete, let's pick for now $n=3$ (Figure~\ref{fig:transfer} also shows the $n=3$ case).
-First we train
-
-\begin{itemize}
-\item A control network \net{R3B} with the first $3$ layers fixed to random filters and all higher layers trained to classify images from dataset \dB.
-\end{itemize}
-
-Then we define and train the following two networks
+%First we train 
+%\begin{itemize}
+%\item A control network \net{R3B} with the first $3$ layers fixed to random filters and all higher layers trained to %classify images from dataset \dB.
+%\end{itemize}
+First, we define and train the following two networks:
 
@@
 The five higher layers are initialized randomly and trained toward dataset \dB.
-Here we're only using data from \dB and layers from a network \net{baseB}, that was trained on \dB.
-This may seem a little strange, but we actually need it as an additional control for the below transfer network.
+Here we're only using data from \dB and layers from a network \net{baseB} that was trained on \dB.
+This may seem a little strange, but we actually need it as an additional control for the next transfer network.
 
@@
 Intuitively, here we're copying the first $3$ layers from the wrong dataset, \dA,  and then trying to learn higher layer features on top of them to classify \dB.
-If this works well, we'll say that those first three layers are general, at least with respect to \dB, and if not, we'll say they are specific to dataset \dA
+If this works well, we'll say that those first three layers are general, at least with respect to \dB, and if not, we'll say they are specific to \dA.
 \end{itemize}
@@
 \begin{itemize}
-\item A \emph{selffer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
-\item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn
+\item A \emph{selffer} network \net{B3B^+} just like \net{B3B}, but where all layers learn.
+\item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn.
 \end{itemize}
 
-Figure~\ref{fig:transfer} shows the networks created for $n = 3$, but we repeated this process for all $n$ in $\{1, 2, \ldots, 7\}$\footnote{Note that $n=8$ doesn't make sense in any case: \net{B8B} is just \net{baseB}, \net{R8B} is just a completely retrained version of \net{baseB}, and \net{A8B} would have no hope of working, because nothing would be trained and the 500 softmax neurons would not match between \dA and \dB.} and in both directions, i.e.
+Figure~\ref{fig:transfer} shows in the bottom two positions the networks created for $n = 3$, but we repeated this process for all $n$ in $\{1, 2, \ldots, 7\}$\footnote{Note that $n=8$ doesn't make sense in any case: \net{B8B} is just \net{baseB}, \net{R8B} is just a completely retrained version of \net{baseB}, and \net{A8B} would have no hope of working, because nothing would be trained and the 500 softmax neurons would not match between \dA and \dB.} and in both directions, i.e.
 transferring from \dA to \dB and \dB to \dA.
@@
 \caption{Overview of the experimental treatments and controls.
-\emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \citep{Krizhevsky-2012}.
+\emph{Top two rows:} The base convnets are trained using standard supervised backprop and randomly initializations.
 Training occurs on only half the dataset (e.g.
-dataset A) for consistency with the experimental treatments.
-The baseline control is repeated for each half of the dataset (A and B).
+dataset \dA) for consistency with the experimental treatments.
+The baseline control is repeated for each half of the dataset (\dA and \dB).
 The labeled rectangles (e.g.
-$W_{A1}$) represent the weight vector for that layer.
-That the rectangle is colored indicates that the weight layer has been trained on the dataset of that color (e.g.
-dataset A).
+$W_{A1}$) represent the weight vector for that layer, with the color indicating which dataset the layer was originally trained toward.
 The vertical, ellipsoidal bars represent neural activations that occur when the network is activated.
 \emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern).
-The weights of the first $N$ layers of the network are frozen (locked), meaning they do not change during training.
+The weights of the first $N$ layers of the network are locked, meaning they do not change during training.
 The remaining layers are trained as normal on half the dataset.
@@
 In this control the first $N$ weight layers of the network are copied from a base network (e.g.
-one trained on dataset B) and then the entire network is trained on that same dataset (in this example, dataset B).
-These layers are either locked during training (in the ``frozen selfer treatments'') or allowed to further fine-tune on the new data set (in the ``fine-tuned selfer treatments''), meaning that normal training occurs in those layers after initialization.
-The weights of layers after the first $N$ layers are initialized randomly and then allowed to train normally.
-This treatment tests whether filters at different layers need to co-adapt during training, or if they can be trained asynchronously.
-\emph{Fifth row:} The ``transfer network'' experimental treatment is the same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.
-B) and then the entire network is trained on the \emph{other} half of the dataset (e.g.
-dataset A).
+one trained on dataset \dB) and then the entire network is trained on that same dataset (in this example, dataset \dB).
+These layers are either locked during training (in the ``locked selfer treatments'') or allowed to train as usual (in the ``fine-tuned selfer treatments'').
+The weights of layers after the first $N$ layers are initialized randomly and then allowed to train as usual.
+This treatment exposes co-adaptation that can only be discovered when filters at different layers are trained together.
+\emph{Fifth row:} The ``transfer network'' experimental treatment.
+Same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.
+\dA) and then the entire network is trained on the \emph{other} half of the dataset (e.g.
+dataset \dB).
 This treatment tests transfer learning.}
@@
 For example, there happen to be many types of certain animals included in the dataset, particularly dogs and cats, like these 13 classes from the biological family \emph{Felidae}:
-
-{
-\small
-\begin{verbatim}
-   ID        Description
-   n02123045 tabby, tabby cat
-   n02123159 tiger cat
-   n02123394 Persian cat
-   n02123597 Siamese cat, Siamese
-   n02124075 Egyptian cat
-   n02125311 cougar, puma, catamount, mountain lion, Felis concolor
-   n02127052 lynx, catamount
-   n02128385 leopard, Panthera pardus
-   n02128757 snow leopard, ounce, Panthera uncia
-   n02128925 jaguar, panther, Panthera onca, Felis onca
-   n02129165 lion, king of beasts, Panthera leo
-   n02129604 tiger, Panthera tigris
-   n02130308 cheetah, chetah, Acinonyx jubatus
-\end{verbatim}
-}
+% TODO
+% long version
+%{
+%\small
+%\begin{verbatim}
+%   ID        Description
+%   n02123045 tabby, tabby cat
+%   n02123159 tiger cat
+%   n02123394 Persian cat
+%   n02123597 Siamese cat, Siamese
+%   n02124075 Egyptian cat
+%   n02125311 cougar, puma, catamount, mountain lion, Felis concolor
+%   n02127052 lynx, catamount
+%   n02128385 leopard, Panthera pardus
+%   n02128757 snow leopard, ounce, Panthera uncia
+%   n02128925 jaguar, panther, Panthera onca, Felis onca
+%   n02129165 lion, king of beasts, Panthera leo
+%   n02129604 tiger, Panthera tigris
+%   n02130308 cheetah, chetah, Acinonyx jubatus
+%\end{verbatim}
+%}
+% short version
+\{\texttt{tabby cat, tiger cat, Persian cat, Siamese cat, Egyptian cat, mountain lion, lynx, 
+leopard, snow leopard, jaguar, lion, tiger, cheetah}\}
 
@@
 When generalizing to the other half, we would expect that the new high-level felid detectors trained on top of fixed old low-level felid detectors would work well.
-
 For comparison, we've also created a special split of the dataset into two halves that are as far apart from each other as possible: one category containing only \emph{natural} classes and another containing \emph{man-made} objects.
@@
 
-\edit{mention faster training here}
+% TODO
+%\edit{mention faster training here}
 
 \section{Details of Experimental Setup}
+\label{sec:setup}
 
@@
 We decided to use the original architecture from \cite{Krizhevsky-2012} not to maximize absolute performance, but to study transfer results on what is probably the most popular single architecture, so that our results will be comparable, extensible, and useful to the largest number of other researchers.
-We actually expect none of the qualitative results presented here to depend at all on small architecture tweaks.
-
-To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \citep{donahue+jia-2013-arxiv}.
-We followed \citet{donahue+jia-2013-arxiv} in making a few minor departures from \cite{Krizhevsky-2012}: we skip the data augmentation trick of adding random multiples of principle components of pixel RGB values, which produced only a $1\%$ improvement in the original paper, and we warped images to $256\times 256$ instead of scaling to keep the aspect ratio and then cropping.
+We expect none of the qualitative results presented here to depend at all on small architecture tweaks.
+To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \citep{Jia13caffe}.
+% TODO consider fitting if possible
+%We followed \citet{donahue+jia-2013-arxiv} in making a few minor departures from \cite{Krizhevsky-2012}: we skip the data augmentation trick of adding random multiples of principle components of pixel RGB values, which produced only a $1\%$ improvement in the original paper, and we warped images to $256\times 256$ instead of scaling to keep the aspect ratio and then cropping.
 In another difference, we placed the Local Response Normalization layers just \emph{after} the pooling layers, instead of before them.
@@
 
-For clarity of presentation, we list all hyperparameter selections in two tables: layer sizes and locations in Table~\ref{tab:network_architecture} and weight initialization and learning rate details in Table~\ref{tab:learning_hyperparams}.
-In the first table, a feedforward pass proceeds from top to bottom, left to right.
-Because code is often more clear than text, we've also made all code and parameter files necessary to reproduce these experiments available on \url{http://github.com/...removed_for_review...}.
+% TODO: fit this in
+%For clarity of presentation, we list all hyperparameter selections in two tables: layer sizes and locations in %Table~\ref{tab:network_architecture} and weight initialization and learning rate details in %Table~\ref{tab:learning_hyperparams}.
+In the first table, a feedforward pass proceeds from top to bottom, left to %right.
 
-\begin{table}[t]
-\caption{Convolutional Network architecture sizes and hyperparameters.
+%\begin{table}[h]
+%\caption{Convolutional Network architecture sizes and hyperparameters.
 Conv stands for Convolutional layers.
@@
 Stride?} LRN stands for local response normalization \citep{Krizhevsky-2012}.}
-\label{tab:network_architecture}
-\begin{center}
-\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
-\hline
-       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
-name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
-\hline
-conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
-conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
-conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
-conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
-conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
-fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
-fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
-fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
+%\label{tab:network_architecture}
+%\begin{center}
+%% TODO
+%% Add padding back in
+%\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
+%\hline
+%%       &      & filter & number  &        &        &     &         & Maxpool        & LRN        \\
+%%name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & (size,$\alpha$,$\beta$) \\
+%%\hline
+%%conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
+%%conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
+%%conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
+%%conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
+%%conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
+%%fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
+%%fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
+%%fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
+%        & filter & number  &        &        &     &         & Maxpool        & LRN        \\
+%name    & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & (size,$\alpha$,$\beta$) \\
+%\hline
+%conv1   & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
+%conv2   & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
+%conv3   & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
+%conv4   & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
+%conv5   & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
+%fc6     &        & 4096    & 1      &        & R   & *       &                &                   \\
+%fc7     &        & 4096    & 1      &        & R   & *       &                &                   \\
+%fc8     &        & 1000    & 1      &        & S   &         &                &                   \\
+%\hline
+%\end{tabular}
+%\end{center}
+%\end{table}
 
-\begin{table}[t]
-\caption{Parameter initializations and learning rates. \todo{JY: I expanded the table headings (we have the space). Please check that I did so accurately. I had to guess on most.}}
-\label{tab:learning_hyperparams}
-\begin{center}
-\begin{tabular}{|r|l|l|l|l|l|l|}
-\hline
-       & \multicolumn{3}{c|}{\bf Weight}     &  \multicolumn{3}{c|}{\bf Bias}       \\
-\cline{2-7}
-       & Gaussian Std. Dev.   & Local Response-multiplier & decay &  const  & Local Response  & decay \\
-\hline
-conv1  & .01    & 1       & y     &  0      & 2   & n     \\
-conv2  & .01    & 1       & y     &  1      & 2   & n     \\
-conv3  & .01    & 1       & y     &  0      & 2   & n     \\
-conv4  & .01    & 1       & y     &  1      & 2   & n     \\
-conv5  & .01    & 1       & y     &  1      & 2   & n     \\
-fc6    & .005   & 1       & y     &  1      & 2   & n     \\
-fc7    & .005   & 1       & y     &  1      & 2   & n     \\
-fc8    & .01    & 1       & y     &  0      & 2   & n     \\ 
-\hline
-\end{tabular}
-\end{center}
-\end{table}
+%\begin{table}[t]
+%\caption{Parameter initializations and learning rates. \todo{JY: I expanded the table headings (we have the space). Please check that I did so accurately. I had to guess on most.}}
+%\label{tab:learning_hyperparams}
+%\begin{center}
+%\begin{tabular}{|r|l|l|l|l|l|l|}
+%\hline
+%       & \multicolumn{3}{c|}{\bf Weight}     &  \multicolumn{3}{c|}{\bf Bias}       \\
+%\cline{2-7}
+%       & Gaussian Std. Dev.   & Local Response-multiplier & decay &  const  & Local Response  & decay \\
+%\hline
+%conv1  & .01    & 1       & y     &  0      & 2   & n     \\
+%conv2  & .01    & 1       & y     &  1      & 2   & n     \\
+%conv3  & .01    & 1       & y     &  0      & 2   & n     \\
+%conv4  & .01    & 1       & y     &  1      & 2   & n     \\
+%conv5  & .01    & 1       & y     &  1      & 2   & n     \\
+%fc6    & .005   & 1       & y     &  1      & 2   & n     \\
+%fc7    & .005   & 1       & y     &  1      & 2   & n     \\
+%fc8    & .01    & 1       & y     &  0      & 2   & n     \\ 
+%\hline
+%\end{tabular}
+%\end{center}
+%\end{table}
 
-We used stochastic gradient descent (SGD) with momentum.
+% TODO: reinsert
+%We trained used stochastic gradient descent (SGD) with momentum.
 Each iteration of SGD used a batch size of 256, momentum 0.9, and multiplicative weight decay (for those weights with weight decay enabled) of 0.0005 per iteration.
@@
 These selections were made after looking at the learning curves for the base case and estimating at which points in each region of constant learning rate the learning had plateaued and thus annealing could take place.
-\edit{A typical learning curve is shown in Figure~\ref{typical_learning}.}
+This faster training schedule was only used for the natural vs. man-made experiments in Section~\ref{sec:experiments_random_nm}.
 
-\editbox{
-Figure {typical\_learning}
-(( make this figure, if important, once reduced-1300-2 run is done ))
-}
+%\edit{A typical learning curve is shown in Figure~\ref{typical_learning}.}
+%
+%\editbox{
+%Figure {typical\_learning}
+%(( make this figure, if important, once reduced-1300-2 run is done ))
+%}
 
@@
 As our goal is not to improve the state of the art, but to investigate properties of transfer, we were content with this level of performance.
+
+Because code is often more clear than text, we've also made all code and parameter files necessary to reproduce these experiments available on \url{http://github.com/...removed_for_review...}.
 
@@
 
-As mentioned earlier, we did two sets of experiments.
-The main experiment using random random \dA/\dB splits is discussed in Section~\ref{sec:experiments_ab}, and the two comparison cases using random filters and the Natural/Man-made split is presented in Section~\ref{sec:experiments_random_nm}.
+We performed two sets of experiments.
+The main experiment using random \dA/\dB splits is discussed in Section~\ref{sec:experiments_ab}, and the two comparison cases using random filters and the Natural/Man-made split is presented in Section~\ref{sec:experiments_random_nm}.
 
@@
 
-\begin{figure}[htpb]
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=1\linewidth]{plots/result_transfer_crop.pdf}
-\includegraphics[width=1\linewidth]{plots/result_transfer_lines_crop.pdf}
+\includegraphics[width=.9\linewidth]{plots/result_transfer_crop.pdf}
+\includegraphics[width=.9\linewidth]{plots/result_transfer_lines_crop.pdf}
 \end{center}
-\caption{Accuracy of each treatment and control.
+\caption{The distilled results from the main experiment in this paper, see the text for detail.
 \emph{Top panel:} Raw data.
-\emph{Bottom panel}: Lines connect the medians of each treatment.
-Shaded areas and text highlight key takeaway messages.
-\todo{This is the min.
-required if we explain the figure in the main text.}
+\emph{Bottom panel}: Lines connecting the means of each treatment.
+Shaded areas and numbers refer to which interpretation of Section~\ref{sec:experiments_ab} applies.
 }
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=1\linewidth]{plots/result_random_nm_combined_crop.pdf}
+\includegraphics[width=.7\linewidth]{plots/result_random_nm_combined_crop.pdf}
 \end{center}
-\caption{\edit{Caption here...}}
+\caption{Performance degredation vs.
+layer; see text for details.
+(top left): random fixed features.
+(top right): a manual split of ImageNet into natural vs.
+man-made groups.
+(bottom): the top two plots normalized by their base performance and compared to the \dA/\dB split from Section~\ref{sec:experiments_ab} (in red).}
 \label{fig:random_and_nm}

### 2014-06-06 paper/body.tex
small edits

--- 2014-06-06 paper/body.tex
@@
 
-\section{Generality vs. Specificity as transfer from one dataset to another}
+\section{Generality vs. specificity measured as transfer performance}
 \label{sec:definition}
@@
 We say these features are general if they are useful for many different tasks or specific if they are useful only for a few.
-We can measure the specificity of a set of features by training it on one task \dA and then using it for another task \dB.
+We can measure the specificity of a set of features by training the set on one task \dA and then using the feature set for another task \dB.
 
-Of course, this definition depends on the distance between \dA and \dB.
-In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset.
-\edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.
+Of course, this definition depends on the similarity, or distance, between \dA and \dB.
+In this paper, we take tasks \dA and \dB to be classifying different, non-overlapping subsets of a particular dataset.
+These subsets could be chosen such that they are similar (e.g.
+by randomly splitting a large dataset into two smaller datasets), or they could be chosen to be different (e.g.
+by choosing the subsets to be maximally different).
+%This is only one possible way of sampling tasks \dA and \dB.
 

### 2014-06-06 paper/body.tex
small edits

@@
 
-Of course, this definition depends on the similarity, or distance, between \dA and \dB.
+Of course, this definition depends on the similarity (distance) between \dA and \dB.
 In this paper, we take tasks \dA and \dB to be classifying different, non-overlapping subsets of a particular dataset.
@@
 
-All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{} except for the last softmax layer, which outputs 500 classes instead of 1000.
+All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section, are the same, namely the sizes described in Section~\ref{} \todo{fill in this empty ref} except for the last softmax layer, which outputs 500 classes instead of 1000.
 

### 2014-06-06 paper/body.tex
further cuts and drawing reduction

@@
 %In fact, this paper's authors are now used to checking for Gabor features in the first layer simply to assure ourselves that the training is at least partially working.
-This phenomenon occurs not only for different datasets, but even with very different training objectives, from supervised image classification \citep{Krizhevsky-2012} to unsupervised sparse representation learning\cite{Le-2011-ICA}.
+This phenomenon occurs not only for different datasets, but even with very different training objectives, from supervised image classification \citep{Krizhevsky-2012} to unsupervised sparse representation learning \citep{Le-2011-ICA}.
 
@@
 
-Once one has general features from some layer of a \emph{base} network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \citep{donahue+jia-2013-arxiv}.
+Once one has general features from some layer of a \emph{base} network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \citep{caruana95,Bengio+al-AI-2011-small,UTLC+DL+tutorial-2011-small,donahue+jia-2013-arxiv}.
 The usual course is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second \emph{target} task.
-When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left \emph{frozen}, meaning that they do not change during training on the new task.
+When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen, meaning that they do not change during training on the new task.
 In cases where the target dataset is smaller than the base dataset, fine-tuning the base features may result in overfitting, so the features are often left frozen.
@@
 Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch.
-We compare results from each of these two techniques --- fine-tuned features or frozen features --- below.
+We compare results from each of these two domains --- fine-tuned features or frozen features --- in a later section.
 
@@
 These networks, which we call \net{baseA} and \net{baseB}, are shown in the top two positions of Figure~\ref{fig:transfer}.
-
-All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{sec:setup} except for the last softmax layer, which outputs 500 classes instead of the usual 1000.
-
-We then choose an $n$ from $\{1, 2, \ldots, 7\}$ and train and compare several networks.
+% TODO reinsert
+%All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{sec:setup} except for the last softmax layer, which outputs 500 classes instead of the usual 1000.
+We then choose an $n$ from $\{1, 2, \ldots, 7\}$ and train and compare several new networks.
 To make the discussion more concrete, let's pick for now $n=3$ (Figure~\ref{fig:transfer} also shows the $n=3$ case).
@@
 
-Finally, we also train fine-tuned versions of the two above networks:
+Then we create and train fine-tuned versions of the two above networks:
 
@@
 For example, \cite{Zeiler+et+al-arxiv2013b} found that it is better to decrease the first layer filters sizes from $11\times 11$ to $7\times 7$ and to use a smaller stride of $2$ instead of $4$.
-When beginning this study we faced the decision of exactly which convolutional architecture to use for our experiments.
-We decided to use the original architecture from \cite{Krizhevsky-2012} not to maximize absolute performance, but to study transfer results on what is probably the most popular single architecture, so that our results will be comparable, extensible, and useful to the largest number of other researchers.
+%When beginning this study we faced the decision of exactly which convolutional architecture to use for our experiments.
+For this study we decided to use the original architecture from \cite{Krizhevsky-2012} as provided in the reference implementation in Caffe, a library for training convolutional models on a GPU \citep{Jia13caffe}.
+We aim not to maximize absolute performance, but to study transfer results on what is probably the most popular single architecture, so that our results will be comparable, extensible, and useful to the largest number of other researchers.
+%To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \citep{Jia13caffe}.
 We expect none of the qualitative results presented here to depend at all on small architecture tweaks.
-To this end, we used the hyperparameters provided in the reference implementation of  \cite{Krizhevsky-2012} with Caffe, a library for training convolutional models on a GPU \citep{Jia13caffe}.
 % TODO consider fitting if possible
@@
 For the bulk of the experiments in this paper, the master learning rate was started at 0.01, annealed over the course of training by dropping it by a factor of 10 every 100,000 iterations, and learning was stopped after 450,000 iterations.
-All training was done on NVidia K20 GPUs.
+%All training was done on NVidia K20 GPUs. 
 Each iteration took about 1.7 seconds, meaning that the whole training procedure for a single network takes 9.5 days.
-
 Because occupying a whole GPU for this long was cumbersome, we also devised a set of hyperparameters to allow faster learning by boosting the learning rate by 25\% to 0.0125, annealing by a factor of 10 after only 64,000 iterations, and stopping after 200,000 iterations.
@@
 As our goal is not to improve the state of the art, but to investigate properties of transfer, we were content with this level of performance.
-
 Because code is often more clear than text, we've also made all code and parameter files necessary to reproduce these experiments available on \url{http://github.com/...removed_for_review...}.
@@
 layers     & over        & over \\
-aggregated & \net{baseA} & selfer \net{AnA^+} \\
+aggregated & \net{baseA} & selffer \net{AnA^+} \\
 \hline

### 2014-06-06 paper/body.tex
caption cuts

@@
 
-\begin{figure}[htpb]
+\begin{figure}[t]
 \begin{center}
@@
 The vertical, ellipsoidal bars represent neural activations that occur when the network is activated.
-\emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern).
+%HERE\emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern).
 The weights of the first $N$ layers of the network are locked, meaning they do not change during training.
@@
 A replicate (not pictured) is performed on the other half of the dataset.
-\emph{Fourth row:} The ``selfer network'' control.
+\emph{Third row:} The ``selfer network'' control.
 In this control the first $N$ weight layers of the network are copied from a base network (e.g.
@@
 This treatment exposes co-adaptation that can only be discovered when filters at different layers are trained together.
-\emph{Fifth row:} The ``transfer network'' experimental treatment.
+\emph{Fourth row:} The ``transfer network'' experimental treatment.
 Same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g.

### 2014-06-06 paper/body.tex
small change

@@
 \begin{enumerate}
-\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}).
-We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
-Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
-\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves.
-In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
-\item We show how the transferability gap grows as the distance between base
-task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009} (Section~\ref{sec:experiments_random_nm}).
-\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
+\item We introduce a way to quantify the degree to which a particular layer is general or specific: how well features at a certain layer transfer from one dataset to another (Section~\ref{sec:definition}).
+We test this proposed measure on a large convnet trained on the ImageNet dataset.
+These experiments also reveal the transition from general to specific layers (Section~\ref{sec:experiments}).
+Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \citep{donahue+jia-2013-arxiv}, but here we systematically characterize the general to specific transition, which yields the next three results.
+\item We experimentally show two separate issues that cause performance declines from transferred features: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers, and the specificity of the features themselves.
+We show how different effects dominate at different layers of the network (Section~\ref{sec:experiments_ab}).
+\item We show how the transferability gap grows as the similarity between base
+task and target task decreases. 
+\item We compare both frozen and fine-tuning transfer to using random filters: we find that random filters do not work as well on the large ImageNet dataset as they have been reported to for smaller datasets \citep{Jarrett-ICCV2009}.
+\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better performance, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
 \end{enumerate}

### 2014-06-06 paper/body.tex

@@
 \begin{center}
-\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
+\includegraphics[width=.8\linewidth]{drawings/transfer.pdf}
 \end{center}
 \caption{Overview of the experimental treatments and controls.
-\emph{Top two rows:} The base convnets are trained using standard supervised backprop and randomly initializations.
-Training occurs on only half the dataset (e.g.
-dataset \dA) for consistency with the experimental treatments.
+\emph{Top two rows:} The base convnets are trained using standard supervised backprop on only half of the dataset (\dA or \dB).
 The baseline control is repeated for each half of the dataset (\dA and \dB).
@@
 \begin{center}
-\includegraphics[width=.9\linewidth]{plots/result_transfer_crop.pdf}
-\includegraphics[width=.9\linewidth]{plots/result_transfer_lines_crop.pdf}
+\includegraphics[width=.85\linewidth]{plots/result_transfer_crop.pdf}
+\includegraphics[width=.85\linewidth]{plots/result_transfer_lines_crop.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=.7\linewidth]{plots/result_random_nm_combined_crop.pdf}
+\includegraphics[width=.65\linewidth]{plots/result_random_nm_combined_crop.pdf}
 \end{center}

### 2014-06-12 paper/body.tex
changes from Yoshua

@@
 We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
-Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
+Others have loosely addressed the question of generality by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
 \item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves.
@@
 \end{center}
-\caption{Performance degredation vs.
+\caption{Performance degradation vs.
 layer; see text for details.

### 2014-06-12 paper/body.tex
Changes from Jeff

--- 2014-06-06 paper/body.tex
@@
 These experiments also reveal the transition from general to specific layers (Section~\ref{sec:experiments}).
-Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \citep{donahue+jia-2013-arxiv}, but here we systematically characterize the general to specific transition, which yields the next three results.
+Others have loosely addressed the question of generality by showing how features from higher layers in a convnet can be transferred to new tasks \citep{donahue+jia-2013-arxiv}, but here we further characterize the general to specific transition, which yields the next three results.
 \item We experimentally show two separate issues that cause performance declines from transferred features: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers, and the specificity of the features themselves.
@@
 task and target task decreases.
-\item We compare both frozen and fine-tuning transfer to using random filters: we find that random filters do not work as well on the large ImageNet dataset as they have been reported to for smaller datasets \citep{Jarrett-ICCV2009}.
-\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better performance, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
+\item We further compare both frozen and fine-tuned transfer to using random filters, which we find not to work as well on the large ImageNet dataset as they have been reported to \citep{Jarrett-ICCV2009} for smaller datasets (Section~\ref{sec:experiments_random_nm}).
+\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better generalization, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
 \end{enumerate}
@@
 We say these features are general if they are useful for many different tasks or specific if they are useful only for a few.
-We can measure the specificity of a set of features by training it on one task \dA and then using it for another task \dB.
-Of course, this definition depends on the distance between \dA and \dB. In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset,
+We can measure the specificity of a set of features by training the set on one task \dA and then using the feature set for another task \dB.
+Of course, this definition depends on the similarity between \dA and \dB. In this paper we take tasks \dA and \dB to be classifying different non-overlapping subsets of a particular dataset.
+These subsets can be chosen in particular ways so that they are as similar to or as different from each other as possible.
 %  \edit{while varying the semantic distance between \dA and \dB?} This is only one possible way of sampling tasks \dA and \dB.
-%The dataset we use is from the
+The dataset we use is
 ImageNet, as released in the Large Scale Visual Recognition Challenge 2012 (ILSVRC2012) \citep{imagenet_cvpr09}.

### 2014-06-12 paper/body.tex
minor further tweaks

@@
 On the other hand, if the target dataset is large enough, the base features can be fine-tuned to the new task.
-Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch.
+Of course, if the target dataset is very large, there would be little need to transfer because the lower level filters could just be learned from the target dataset.
 We compare results from each of these two techniques --- fine-tuned features or frozen features --- below.
@@
 \begin{enumerate}
-\item We introduce a way to quantify the degree to which a particular layer is general or specific: how well features at a certain layer transfer from one dataset to another (Section~\ref{sec:definition}).
+\item We introduce a way to quantify the degree to which a particular layer is general or specific: how well features at that layer transfer from one dataset to another (Section~\ref{sec:definition}).
 We test this proposed measure on a large convnet trained on the ImageNet dataset.
@@
 We show how different effects dominate at different layers of the network (Section~\ref{sec:experiments_ab}).
-\item We show how the transferability gap grows as the similarity between base
+\item We quantify how the transferability gap grows as the similarity between base
 task and target task decreases.

### 2014-08-11 paper/reviews/rebuttal.txt
rebuttal draft

We would like to thank the reviewers for their encouraging feedback and insightful comments. All reviewers seemed to understand the study and its main results exactly as we interpreted them, so the below comments to reviewers are only minor.

REVIEWER 1

> On the other side, this paper seems a bit empirical, in
> the sense that experiments are carried out on some manual 
> decisions (such as split of source and target tasks).

Admittedly it was our choice to perform separation into natural vs. man-made subsets. However, given the hierarchical class structure of WordNet and ImageNet, these two subsets were the only two large exclusive subsets available. This can be seen in the below list of the top 20 subsets of classes, sorted by number of classes (first column) in each subset:

90 n03122748 - covering
100 n03094503 - container
118 n02084071 - dog, domestic dog, Canis familiaris
123 n01317541 - domestic animal, domesticated animal
130 n02083346 - canine, canid
130 n03183080 - device
158 n02075296 - carnivore
212 n01886756 - placental, placental mammal, eutherian, eutherian mammal
218 n01861778 - mammal, mammalian
337 n01466257 - chordate
337 n01471682 - vertebrate, craniate
358 n03575240 - instrumentality, instrumentation
398 n00015388 - animal, animate being, beast, brute, creature, fauna
410 n00004258 - living thing, animate thing
410 n00004475 - organism, being
522 n00021939 - artifact, artefact
949 n00003553 - whole, unit
958 n00002684 - object, physical object
997 n00001930 - physical entity
1000 n00001740 - entity

Starting at the largest subset, "1000 n00001740 - entity", and working backward, the first subset containing close to 50% of the classes is "522 n00021939 - artifact, artefact", and the next is "410 n00004475 - organism, being". Fortunately, these two subsets are mutually exclusive, the first being our "man-made" category and the second our "natural" category. Our only real influence was in choosing what to do with the remaining 1000-522-410=68 classes (Are cooked squash natural or man-made?). We looked at example images from each of the 68 classes and placed them into either task A or B, as we thought best. In our code release, we provide a list of the 551 vs 449 classes in each category, and we highlight those 68 category decisions that were made manually.

> It would be good to see a quantitative criterion analyzing
> the correlation between the two factors raised in the
> paper and the final performance. Of course, the authors
> have fairly acknowledged so, and have not overclaimed
> anything beyond what is presented.

This is an interesting idea, though we're not sure exactly what sort of quantitative criterion would be most helpful. Could you elaborate on what you envision?

We think this suggestion might be to create a model in which we regress a dependent variable, the transfer performance (difference or ratio vs the base case), onto two independent variables, (1) the semantic similarity between task A and task B and (2) the chosen layer for transfer.

In this interpretation we would need to come up with a measure for (1) that does not depend on the transfer performance. For example, one might get a handle on (1) by measuring the number of edges in the WordNet graph one must traverse to get from class A_i to class B_j, and then use the average over all classes in A and B as the distance between task A and task B. This would give some notion of how similar A and B are, and we could then show how transfer is worse for more distance classes.

However, we're not sure this would be a useful model. We would be modeling a handful of points in three dimensions, and actually these are exactly the points already shown in the bottom plot of Figure 3 (along the upper two lines with circles). These points are already plotted along (2) the layer-number axis, and all this new model would add would be a second independent axis, (1) "semantic distance between tasks A and B", which would separate the points along that dimension. Unfortunately, along that new dimension we would have data at *only two* locations, the distance value corresponding to random splits, and the distance value corresponding to the nat/man split.

While we could fit such an ad hoc model with only two points along one dimension, we suspect one would gain no insight from the model beyond what one can already obtain directly from Figure 3. Of course, if we had many more points along this new axis, the model could become interesting, but this would require quite a few more experiments and methods of generating tasks A and B with finely varying semantic separation. Which is to say, this would be a great idea for future work.

REVIEWER 2

> Many interesting observations are made which were not
> previously reported, particularly results #3 and #5 in
> section 4.1.

This is just a minor point, but did you actually mean that #2 was surprising, not #3?

We ask because we found #2 and #5 the most surprising, and we believe both have not previously been reported. On the other hand, conclusion #3 -- that layers copied from a previous solution and fine-tuned toward the original task do not suffer a performance penalty or enjoy a performance gain -- we found not to be surprising. However, if you think that this is surprising, we'd love to hear why. If we have missed any discussion points related to this conclusion, it would be great to include them!

### 2014-08-11 paper/reviews/rebuttal.txt
rebuttal updates from Jeff, Hod, Yoshua comments

@@
 
-Admittedly it was our choice to perform separation into natural vs.
+Admittedly, it was our choice to perform separation into natural vs.
 man-made subsets.
 However, given the hierarchical class structure of WordNet and ImageNet, these two subsets were the only two large exclusive subsets available.
-This can be seen in the below list of the top 20 subsets of classes, sorted by number of classes (first column) in each subset:
+This can be seen in the below list of the top 14 subsets of classes, sorted by number of classes (first column) in each subset:
 
-90 n03122748 - covering
-100 n03094503 - container
-118 n02084071 - dog, domestic dog, Canis familiaris
-123 n01317541 - domestic animal, domesticated animal
-130 n02083346 - canine, canid
-130 n03183080 - device
 158 n02075296 - carnivore
@@
 
-Starting at the largest subset, "1000 n00001740 - entity", and working backward, the first subset containing close to 50% of the classes is "522 n00021939 - artifact, artefact", and the next is "410 n00004475 - organism, being".
-Fortunately, these two subsets are mutually exclusive, the first being our "man-made" category and the second our "natural" category.
+Starting at the largest subset "1000 n00001740 - entity" containing all 1000 classes and working backward, the first subset containing approximately 50% of the classes is "522 n00021939 - artifact, artefact", and the next is "410 n00004475 - organism, being".
+Fortunately for this study, these two subsets are mutually exclusive, the first became our "man-made" category and the second our "natural" category.
 Our only real influence was in choosing what to do with the remaining 1000-522-410=68 classes (Are cooked squash natural or man-made?).
-We looked at example images from each of the 68 classes and placed them into either task A or B, as we thought best.
+We looked at example images from each of the 68 classes and placed them into either "natural" or "man-made", as we thought best.
 In our code release, we provide a list of the 551 vs 449 classes in each category, and we highlight those 68 category decisions that were made manually.
+
+We initially left most of this discussion out of the paper to save space, but thanks to this comment, we realize that in its absence the split does seem arbitrary.
+Thus, we will include this discussion in the final version.
 
@@
 
-This is an interesting idea, though we're not sure exactly what sort of quantitative criterion would be most helpful. Could you elaborate on what you envision?
+This is an interesting idea, though we're not sure exactly what sort of quantitative criterion would be most helpful.
+Could you elaborate on what you envision?
+We would be happy to attempt and include such an analysis once we understand exactly what is being suggested.
 
-We think this suggestion might be to create a model in which we regress a dependent variable, the transfer performance (difference or ratio vs the base case), onto two independent variables, (1) the semantic similarity between task A and task B and (2) the chosen layer for transfer.
+The review process is not amenable to back and forth discussion, so to maximize the value of a follow-up response, we'll describe one guess at which model may have been implied.
 
-In this interpretation we would need to come up with a measure for (1) that does not depend on the transfer performance.
-For example, one might get a handle on (1) by measuring the number of edges in the WordNet graph one must traverse to get from class A_i to class B_j, and then use the average over all classes in A and B as the distance between task A and task B.
+We think this suggestion might be to create a model in which we regress a dependent variable, the transfer performance (difference or ratio vs the base case), onto two independent variables, (1) the similarity between task A and task B and (2) the chosen layer for transfer.
+
+In this interpretation we would need to come up with a measure for (1) that does not depend on the transfer performance itself.
+For example, one might get a handle on (1) by training a full 1000-class ImageNet network and then looking at the (A_i,B_j) element of the confusion matrix and then using the average over all classes in A and B as the similarity between task A and task B.
 This would give some notion of how similar A and B are, and we could then show how transfer is worse for more distance classes.
 
-However, we're not sure this would be a useful model.
-We would be modeling a handful of points in three dimensions, and actually these are exactly the points already shown in the bottom plot of Figure 3 (along the upper two lines with circles).
-These points are already plotted along (2) the layer-number axis, and all this new model would add would be a second independent axis, (1) "semantic distance between tasks A and B", which would separate the points along that dimension.
-Unfortunately, along that new dimension we would have data at *only two* locations, the distance value corresponding to random splits, and the distance value corresponding to the nat/man split.
+We would be modeling a handful of points in three dimensions, and actually these are the points already shown in the bottom plot of Figure 3 (along the upper two lines with circles).
+These points are already plotted along (2), the layer-number axis, and all this new model would add would be a second independent axis, (1) "similarity between tasks A and B", which would separate the points along that dimension.
+Unfortunately, along that new dimension we would have data at *only two* locations, the distance value corresponding to random splits, and the distance value corresponding to the natural/man-made split.
 
-While we could fit such an ad hoc model with only two points along one dimension, we suspect one would gain no insight from the model beyond what one can already obtain directly from Figure 3.
-Of course, if we had many more points along this new axis, the model could become interesting, but this would require quite a few more experiments and methods of generating tasks A and B with finely varying semantic separation.
-Which is to say, this would be a great idea for future work.
+While we could fit such a model with only two points along one dimension, we are uncertain if one would gain insight from the model beyond what can already be obtained directly from Figure 3.
+If we had many more points along this new axis, the model could become interesting, but this would require quite a few more computationally expensive experiments and methods of generating tasks A and B with more finely varying semantic separation.
+Which is to say, we think this would be a great idea for future work!
+
+But, again, we are uncertain if this is the type of model the reviewer has suggested, so any clarification would be appreciated.
 
@@
 
-This is just a minor point, but did you actually mean that #2 was surprising, not #3?
+This is just a minor point, but did you actually mean that #2 was surprising, not #3? To summarize the observations:
 
-We ask because we found #2 and #5 the most surprising, and we believe both have not previously been reported.
-On the other hand, conclusion #3 -- that layers copied from a previous solution and fine-tuned toward the original task do not suffer a performance penalty or enjoy a performance gain -- we found not to be surprising.
-However, if you think that this is surprising, we'd love to hear why.
-If we have missed any discussion points related to this conclusion, it would be great to include them!
+#2: Features on multiple levels co-adapt in a way that cannot be relearned from scratch.
+#3: Copying layers from a previous solution and fine-tuning them toward the original task does not lead to a performance penalty or gain.
+#5: Transferred features followed by fine-tuning results in networks that generalize better than those trained directly on the target dataset.
+
+We ask because we found #2 and #5 to be the most surprising, and we believe both have not previously been reported.
+On the other hand, conclusion #3 seemed to be expected, because all layers are optimized for a single task, just starting at a solution previously found using the same data/same task.
+However, if we've missed something and you think that this is surprising given your intuition or any related work you're familiar with, we'd love to hear why, so we could include a refined description of these observations in the paper.

### 2014-08-11 paper/reviews/rebuttal.txt
rebuttal cuts proposed by Jeff and Yoshua

@@
 We would like to thank the reviewers for their encouraging feedback and insightful comments.
-All reviewers seemed to understand the study and its main results exactly as we interpreted them, so the below comments to reviewers are only minor.
+Almost all of the reviewer comments were positive.
+Below we reply to one comment and the one suggestion for a potential change to the paper.
 
@@
 
-We initially left most of this discussion out of the paper to save space, but thanks to this comment, we realize that in its absence the split does seem arbitrary.
+We initially left most of this discussion out of the paper to save space, but thanks to this comment, we realize that in its absence the decisions do seem arbitrary.
 Thus, we will include this discussion in the final version.
@@
 
-The review process is not amenable to back and forth discussion, so to maximize the value of a follow-up response, we'll describe one guess at which model may have been implied.
+To summarize, we plan to make the following changes for a final version of the paper:
 
-We think this suggestion might be to create a model in which we regress a dependent variable, the transfer performance (difference or ratio vs the base case), onto two independent variables, (1) the similarity between task A and task B and (2) the chosen layer for transfer.
+ - Add discussion of motivation behind creation of natural vs. man-made split, suggested by Reviewer 1.
 
-In this interpretation we would need to come up with a measure for (1) that does not depend on the transfer performance itself.
-For example, one might get a handle on (1) by training a full 1000-class ImageNet network and then looking at the (A_i,B_j) element of the confusion matrix and then using the average over all classes in A and B as the similarity between task A and task B.
-This would give some notion of how similar A and B are, and we could then show how transfer is worse for more distance classes.
+ - Possibly add model suggested by Reviewer 1.
 
-We would be modeling a handful of points in three dimensions, and actually these are the points already shown in the bottom plot of Figure 3 (along the upper two lines with circles).
-These points are already plotted along (2), the layer-number axis, and all this new model would add would be a second independent axis, (1) "similarity between tasks A and B", which would separate the points along that dimension.
-Unfortunately, along that new dimension we would have data at *only two* locations, the distance value corresponding to random splits, and the distance value corresponding to the natural/man-made split.
-
-While we could fit such a model with only two points along one dimension, we are uncertain if one would gain insight from the model beyond what can already be obtained directly from Figure 3.
-If we had many more points along this new axis, the model could become interesting, but this would require quite a few more computationally expensive experiments and methods of generating tasks A and B with more finely varying semantic separation.
-Which is to say, we think this would be a great idea for future work!
-
-But, again, we are uncertain if this is the type of model the reviewer has suggested, so any clarification would be appreciated.
-
-REVIEWER 2
-
-> Many interesting observations are made which were not
-> previously reported, particularly results #3 and #5 in
-> section 4.1.
-
-This is just a minor point, but did you actually mean that #2 was surprising, not #3? To summarize the observations:
-
-#2: Features on multiple levels co-adapt in a way that cannot be relearned from scratch.
-#3: Copying layers from a previous solution and fine-tuning them toward the original task does not lead to a performance penalty or gain.
-#5: Transferred features followed by fine-tuning results in networks that generalize better than those trained directly on the target dataset.
-
-We ask because we found #2 and #5 to be the most surprising, and we believe both have not previously been reported.
-On the other hand, conclusion #3 seemed to be expected, because all layers are optimized for a single task, just starting at a solution previously found using the same data/same task.
-However, if we've missed something and you think that this is surprising given your intuition or any related work you're familiar with, we'd love to hear why, so we could include a refined description of these observations in the paper.
+ - Strengthen statistical conclusions by averaging over more randomly initialized trials (trials currently running).

### 2014-08-12 paper/reviews/rebuttal.txt
Rebuttal submitted

@@
 Starting at the largest subset "1000 n00001740 - entity" containing all 1000 classes and working backward, the first subset containing approximately 50% of the classes is "522 n00021939 - artifact, artefact", and the next is "410 n00004475 - organism, being".
-Fortunately for this study, these two subsets are mutually exclusive, the first became our "man-made" category and the second our "natural" category.
+Fortunately for this study, these two subsets are mutually exclusive; the first became our "man-made" category and the second our "natural" category.
 Our only real influence was in choosing what to do with the remaining 1000-522-410=68 classes (Are cooked squash natural or man-made?).
-We looked at example images from each of the 68 classes and placed them into either "natural" or "man-made", as we thought best.
+We looked at example images from each of the 68 classes and placed them into either "natural" or "man-made" as we thought best.
 In our code release, we provide a list of the 551 vs 449 classes in each category, and we highlight those 68 category decisions that were made manually.
@@
 Could you elaborate on what you envision?
-We would be happy to attempt and include such an analysis once we understand exactly what is being suggested.
+We have spent some time discussing how best to implement your suggested analysis, but we concluded that we do not yet understand your suggestion enough to implement it precisely.
+We would be happy to include such an analysis once we understand exactly what is being suggested.
+
+GENERAL
+
+One additional change we plan to make, provided the reviewers do not object, is to add even more replicates of as many experiments as possible to increase the statistical strength of our results.
+Trials are ongoing, and we will add as many data points as our available computation allows.
+
+SUMMARY
 
@@
 
- - Strengthen statistical conclusions by averaging over more randomly initialized trials (trials currently running).
+ - Strengthen statistical conclusions by averaging over more randomly initialized trials.
